\voffset-2cm\hoffset-1.5cm   %% Change here

\documentclass{article}
\pagestyle{empty}
\usepackage[tex4ht]{hyperref}
\hypersetup{colorlinks=false}

\textwidth=17cm\textheight=25cm %% Change here
\parindent=0pt
\addtolength{\parskip}{4pt}
\addtolength{\itemsep}{20pt}
\def\tc{\mathaccent"7017}


\begin{document}


\begin{center}

\textbf{\Large Curriculum vitae of
Vladimir Maz'ya}

\end{center}

\bigskip


%\section*{Curriculum vitae of Vladimir Maz'ya}

\noindent
Dept. of Mathematical Sciences, University of Liverpool, Liverpool L69 7ZL, UK, Honorary Senior Fellow\\
 %Dept. of Mathematics, Ohio State University, 231 W 18th Avenue, Columbus, OH 43210, USA\\ 
Dept. of Mathematics, Link\"oping University,
SE-581 83 Link\"oping, Sweden, Professor Emeritus\\
 % Phone: +46 - 13 - 28 23 73 (off), +46 - 13
%- 21 16 04 (h)
%  Fax: +46 - 13 - 28 57 60
\noindent 

 Email:
        \protect\href{mailto:vlmaz@liverpool.ac.uk}{vlmaz@liverpool.ac.uk} (Liverpool), 
        \protect\href{mailto:vlmaz@mai.liu.se}{vlmaz@mai.liu.se} (Link\"oping) 

  \url{http://www.mai.liu.se/~vlmaz}

%% \begin{tabular}{lll}
%%  Email: & \protect\href{mailto:vlmaz@liverpool.ac.uk}{vlmaz@liverpool.ac.uk} & (Liverpool)\\
%%         & \protect\href{mailto:vlmaz@mai.liu.se}{vlmaz@mai.liu.se} & (Link\"oping) \\
%% \end{tabular}
%% 
%% \begin{tabular}{l}
%%   \url{http://www.mai.liu.se/~vlmaz}
%% \end{tabular}

\medskip

\noindent{\bf Main research interests}
\begin{itemize}
          \item  Linear and non-linear PDEs
       \item  Asymptotic and numerical methods
for PDEs,\\
 including homogenization and boundary elements
       \item  Spectral theory
       \item Harmonic analysis
\item  Approximation theory
       \item  Wavelets
       \item  Elasticity theory
       \item  Function spaces
       \item  Ill-posed problems
       \item  Non-linear potential theory
       \item  Fluid mechanics
       \item  History of mathematics
\end{itemize}

\medskip

\noindent{\bf Education}
\begin{itemize}
       \item 1965 Sci. D. in Mathematics
Leningrad State University, Russia
       \item 1962 Ph. D. in Mathematics Moscow
State University, Russia
       \item 1960 MS in Mathematics Leningrad
State University, Russia
\end{itemize}

\medskip

     \noindent{\bf Employment}
\begin{itemize}

\item September 2004 --\hskip 2mm Professor, Department of Mathematical Sciences, University of Liverpool
\item January, 2004 - June 2008 \hskip 2mm Professor,  Department of Mathematics, Ohio State University
\item September - November 2003 Senior Fellow, Schr\"odinger Institute, Vienna
\item January - June 2003 Visiting Stone Professor, Northeastern University  
\item March - May 2002 Visiting position  Maitre des
Recherches, Institute Henri Poincar\'e, Paris
      \item September - December 1994 Visiting position of Maitre des
Recherches, {\'E}cole  Polytechnique, Palesaux, 1994
      \item 2003  -- \hskip2mm Professor Emeritus, Department of Mathematics,  Link\"oping University, Sweden
\item 1993 - 2002 Professor,
 Department of Mathematics,  Link\"oping 
  University, Sweden
       \item 1990 - 1993 Associate Professor, Department of
Mathematics, 
  Link\"oping University, Sweden
       \item 1986-1990 Head of Laboratory of
Mathematical Models in 
  Mechanics, Leningrad Institute of Engineering Studies of Academy of 
  Sciences USSR
       \item 1968-1972 Professor,  Department of Mathematics,
Leningrad Shipbuilding Institute
       \item 1964-1986 Senior Research
Scientist, Mathematics and Mechanics 
  Institute, Leningrad State University
       \item 1960-1964 Junior Research
Scientist, Mathematics and Mechanics 
  Institute, Leningrad University
\end{itemize}

\medskip

  \noindent{\bf  Honours and Awards}
\begin{itemize}
  
  \item October 2012,  Fellow of the American Mathematical Society.  
  \item July 2009, \href{http://www.lms.ac.uk/activities/prizes_com/citations09.html}
                        {Senior Whitehead Prize of the London Mathematical Society}.
\item  {\it Analysis, Partial Differential Equations and Applications}, 
  \href{http://www.springer.com/birkhauser/mathematics/book/978-3-7643-9897-2}
       {{\it The Vladimir Maz'ya Anniversary Volume}}, 
   Series: Operator Theory: Advances and Applications, Vol. 193, A. Cialdea, F. Lanzara, P.E. Ricci (Eds.), 2009, Birkh\"auser.
 \item {\it Perspectives in Partial Differential Equations, Harmonic Analysis and Applications:}
   \href{http://books.google.com/books?id=XY47d5ZjIhoC&pg=PR7&dq=mitrea+maz%27ya#v=onepage&q=mitrea%20maz%27ya}
      {{\it A Volume in Honor of Vladimir G. Maz'ya's 70th Birthday}}, 
          Proceedings of Symposia in Pure Mathematics, AMS, 2008.
\item 
M.V. Anolik, Yu.D. Burago, Yu.K. Dem’yanovich, S.V. Kislyakov, V.P. Khavin, G.A. Leonov, N.F. Morozov, S.V. Poborchii, N.N. Ural’tseva,
N.A. Shirokov,  
\href{http://www.mai.liu.se/~vlmaz/70th-aniv.pdf}
     {{\it Vladimir Gilelevich Maz'ya}}
{\it (On the Occasion of His 70th Anniversary)}, 
Vestnik Sankt-Peterburgskogo Universiteta. Seriya 1. Matematika, Mekhanika, Astronomiya, 2008, No. 4,  3--6.
\item Nordic-Russian Symposium in honour of Vladimir Maz'ya on the occasion of his 70th birthday, Stockholm, 25th --27th August 2008.
\item Analysis, PDEs and Applications, Conference on the occasion of the 70th birthday of Vladimir Maz'ya, Rome, June 30 - July 3, 2008.
\item  M. S. Agranovich, Yu. D. Burago, B. R. Vainberg, M. I. Vishik, S. G. Gindikin, V. A. Kondrat'ev, V. P. Maslov, S. V. Poborchii, Yu. G. Reshetnyak, V. P. Khavin, M. A. Shubin, {\it Vladimir Gilelevich Maz'ya (on his 70th birthday)}, Russian Math. Surveys 63:1(2008),  189--196. 
\item From the 
  \href{http://www.mai.liu.se/~vlmaz/pdf/people.pdf}
  {Notices of the American Mathematical Society}, 
  May 2005, vol.~\textbf{52}, no. 5
\item May 2004, The Celsius Gold Medal of the Royal Society of Sciences at Uppsala

\item M.S.Agranovich, Yu.D.Burago, V.P.Khavin, V.A.Kondratiev, V.P.Maslov, 
S.M.Nikol'skii, Yu.G.Reshetnyak, M.A.Shubin, B.R.Vainberg, M.I.Vishik, L.R.Volevich,
\href{http://www.mai.liu.se/~vlmaz/VlMaz65.pdf}
     {{\it Vladimir G. Maz'ya. On the occasion of his 65th anniversary}}, 
     Russian J. of Math. Physics, 
{\bf 10}:3 (2003), 239--244. 
   \item  March 2003, Verdaguer Prize  of the
French Academy of Sciences
\item April 2002, Member of the Royal
Swedish Academy of Sciences
       \item Invited 45 min talk at the
         \href{http://www.icm2002.org.cn}
              {International Congress of Mathematicians}, Beijing, 2002
       \item 5th March, 2001, Corresponding
Fellow of the Royal Society of 
  Edinburgh (Scottland's National Academy)
       \item November 1999, Humboldt Research
Prize
       \item \href{http://www.mai.liu.se/~vlmaz/anniversary_collection/anniversary_collection.html}
                  {The Maz'ya Anniversary Collection}, edited by Rossmann, J., 
  Taka{\v c}, P., Wildenhain, G., University of
Rostock, Germany, Birkh{\"a}user 
  Verlag, 1999.
             \item Volume 1: On Maz'ya's Work
in Functional Analysis, 
  Partial Differential Equations and Applications
             \item Volume 2: Rostock Conference
on Functional Analysis, 
  Partial Differential Equations and Applications
\item  \href{http://www.mai.liu.se/~vlmaz/IABEM/C0066.html}
            {Mathematical Aspects of Boundary Element Methods}, dedicated to 
  Vladimir Maz'ya on the occasion of his 60th birthday, edited by Marc 
  Bonnet, Anna-Margarete S{\"a}ndig and
Wolfgang Wendland, Chapman and 
  Hall/CRC Research Notes in Mathematics, London, 1999.
       \item August 31--Sept 4, 1998 A
conference in honour of Vladimir 
  Maz'ya, Functional Analysis, Partial Differential Equations and 
  Applications, Rostock, Germany
       \item May 26--29 1998, Minisymposium
dedicated to V. Maz'ya 
  ``Mathematical Aspects of Boundary Element Methods'' at the IABEM 
  International Symposium on Boundary Element Methods,
{\'E}cole 
  Polytechnique, Palaiseau (Paris), France
       \item Eidus, D., Khvoles, A., Kresin,
G., Merzbach, E., Pr{\"o}ssdorf, 
  S., Shaposhnikova, T., Sobolevskii, P., 
  \href{http://www.mai.liu.se/~vlmaz/60birthday/60birthday.html}
       {{\it Mathematical work of Vladimir Maz'ya}} 
  {\it  (on the occasion of his 60th birthday)}, Funct. Differ. Equ. 4 
  (1997), no. 1-2, 3--11 (1998).
       \item 1990 Doctor honoris causa of the
University of Rostock, Germany
       \item 1962 Prize of the Leningrad
Mathematical Society, Russia
\end{itemize}

\bigskip

 \noindent{\bf Some other professional activities}

\begin{itemize}  

\item Plenary speaker at the Conference on Spectral Theory and Geometric Analysis, July 29 - August 2, 2009, Boston.
\item Plenary speaker at the Seventh Congress of the International Society for Analysis, its Applications and Computation, July 13-18, 2009, London.
\item 2007: Member of the NSF panel {\it Harmonic Analysis and Partial Differential Equations}.
\item Plenary speaker at the British Mathematical Colloquium {\it Mathematics 2005}, 4--7 April, Liverpool
\item Two hour speaker at the Rivi\`ere-Fabes Symposium on Analysis and PDE, Minneapolis, April 2005
\item Plenary speaker at the Congress of the German Mathematical Society (together with Yu. Manin, E. Lieb {\it et al}), September 2003
\item Plenary speaker at the Third Congress of the International Society for Analysis, its Applications and Computation, August 20-25, 2001, Berlin.
\item A member of The Friends of
Mittag-Leffler Institute, 1999-2000
 \item March 21-22, 1999: Plenary
speaker at the France-Israel 
  conference 
  \href{http://www.biu.ac.il/RA/space}
       {Space: Frontiers of Interdisciplinary Research and Applications} 
 dedicated to Alain Bensoussan (the other plenary 
  speakers A. Bensoussan and R. Temam)
       \item March 25-28 1999, Invited address
at the 
\href{http://www.tu-chemnitz.de/mathematik/TMP/programm.html}
  {International Conference on Recent Advances in Analytical and Numerical Treatment 
  of Operator Equations in memory of Siegfried Pr{\"o}ssdorf}

       \item August 16-20 1999, Plenary
lecture at the 
\href{http://www.maths.lth.se/garding80.html}
     {International Conference on Analysis and Mathematical
Physics in honour of Lars G{\aa}rding on his 80th birthday}. (the other
plenary speakers M. Atiyah, 
  M. Birman, L. Boutet de Monvel, J.
Br{\"u}ning, G. Grubb, V. Ivrii, P. D. 
  Lax, J. Sj\"ostrand, M. Solomyak, J. P.
Solovej, A. S. Wightman, D. 
  Yafaev)
       \item October 14-18 1998, Invited
address at the International 
  Symposium Problemi Attuali dell'Analisi e
della Fisica Mathematica 
  dedicato alla Memoria di Gaetano Fichera
\item Visiting position of Maitre des Recherches, \'Ecole Polytechnique, Palesaux, 1994
  \item Organizer and Chairman of two
International Conferences on 
  Applied and Industrial Mathematics,
Link\"oping, Sweden, December 1991 
  and June 1994
      \item One of the fifteen mathematical
addresses at the Wiener 
  Centennial Symposium in Cambridge,
Massachusetts, October 8-15, 1994. 
  (together with J. Bourgain, L. Carleson, L.
Ehrenpreis, V. Guillemin, 
  L. H\"ormander, P. W. Jones, P. Malliavin,
H. P. McKean, Y. Meyer, D. 
  Mumford, Ya. Sinai, E. M. Stein, J.
Sj\"ostrand, H. Widom)
\end{itemize}

 \noindent{\bf Graduate supervising at
Link\"oping University}\\
\begin{itemize}
\item Doctorate:\\
              2002 - J. {\AA}slund, 
              2001 - S. Eilertsen, 
              1997 - M. Langer, 
              1997 - T. Ivanov, 
              1996 - J. Bj\"orn,
              1995 - G. Bastay
% \end{itemize}
 \item Licentiate:\\
%\begin{itemize}             
%\item 
2003 - D. Pettersson,
1999 - J. {\AA}slund,
              1997 - S. Eilertsen,
              1996 - T. Ivanov,
              1995 - M. Langer, H.
{\AA}kermark
%  \end{itemize}
     \item Masters:\\
% \begin{itemize}             
             1998 - J. {\"O}stensson,
              1995 - J. {\AA}slund, S.
Eilertsen, H. Lundmark
\end{itemize}

 \noindent{\bf Graduate supervising at
Liverpool  University}\\
\begin{itemize}
\item MSci:\\
            2005 - M. Nieves
\item PhD:\\
            2007 - M. Nieves            
\end{itemize}

  \noindent{\bf Member of Editorial Boards}
   \begin{itemize}
     \item Complex Variables and Elliptic Equations. An International Journal, USA.
     \item Journal of Mathematical Sciences, New York, Springer 
       (Problemy Matematicheskogo Analiza, St-Petersburg).
      \item International Journal of Pure and Applied Mathematics, Academic Publications, Bulgaria
       \item Zeitschrift f{\"u}r Analysis and
ihre Anwendungen, Hederman Verlag,  Berlin
       \item Potential Analysis, Kluwer
Academic Publishers, the Netherlands
       \item Asymptotic Analysis,
North-Holland, Amsterdam-London-New York-Tokyo
       \item Functional Differential Equations,
The Research Institute, The 
  College of Judea and Samaria, Kedumim-Ariel, Israel
       \item Applicable Analysis, USA
       \item Mathematische Nachrichten, Germany
       
       
\end{itemize}



\bigskip


\noindent{\bf  Books published:}
\begin{itemize}
\item Kresin, G., Maz'ya, V. {\it Maximum Principles and Sharp Constants for Solutions of Elliptic and Parabolic Systems}, vol. 183, 328 pp., American Mathematical Society,
2012.

\item Maz'ya V., Rossmann J., {\it Elliptic Equations in Polyhedral Domains}, American Mathematical Society, 2010.

\item Maz'ya V.,   Soloviev A.,  {\it Boundary Integral Equations on Contours with Peaks}, Birkh\"auser, 2010.

\item Maz'ya V., Shaposhnikova T., {\it Theory of Sobolev Multipliers with
  Applications to Differential and Integral Operators}, Grundlehren der
  Mathematischen Wissenschaften, vol. 337, Springer, 2009.

\item Maz'ya V., Shaposhnikova T., {\it Jacques Hadamard, Legend of  Mathematics}. MCNMO Publishers, Moscow, 2008 (revised,  extended, and  authorized translation from English to Russian).
\item Maz'ya, V. (Editor)
 {\it Sobolev Spaces in Mathematics},  I. Sobolev Type Inequalities, Springer,  2008.
\item Maz'ya, V. (Editor)
 {\it Sobolev Spaces in Mathematics},  II. Applications in Analysis and Partial Differential Equations, Springer,  2008.
\item   Approximate Approximations (with G. Schmidt), American Mathematical Society, 2007.
\item
 Sharp Real-Part Theorems. A Unified approach (with G. Kresin), Lecture Notes in Mathematics, No 1903, Springer, 2007.
\item 
 Imbedding and Extension Theorems for Functions in Non-Lipschitz Domains (with S. Poborchi), St-Petersburg University Publishers, 2007.

\item \href{http://www.mai.liu.se/~vlmaz/books/Had-fr-back.jpg}
           {Jacques Hadamard, un Math\'ematicien Universel}  (with T. Shaposhnikova),
  EDP Sciences, Paris, 2005 (revised and extended translation from English).

\item \href{http://www.mai.liu.se/~vlmaz/books/nikuz.html}
           {Linear Water Waves. A Mathematical Approach} (with N. Kuznetsov 
  and B. Vainberg),  Cambridge University Press, 2002.
\item \href{http://www.mai.liu.se/~vlmaz/books/conical.html}
      {Spectral Problems Associated with Corner Singularities of Solutions to Elliptic Equations} 
      (with V. Kozlov and J. Rossman), 
  Mathematical Surveys and Monographs, vol. 85, American Mathematical 
  Society, 2000.
\item \href{http://www.mai.liu.se/~vlmaz/books/as.html}
        {Asymptotic Theory of Elliptic Boundary Value Problems in 
  Singularly Perturbed Domains}, vol 2 (with S. Nazarov and B. 
  Plamenevskij), Operator Theory. Advances and Applications, vol. 112, 
  XXIII+323, Birkh\" auser, 2000.
   \item \href{http://www.mai.liu.se/~vlmaz/books/as.html}
        {Asymptotic Theory of Elliptic Boundary Value Problems in 
  Singularly Perturbed Domains}, vol 1 (with S. Nazarov and B. 
  Plamenevskij), Operator Theory. Advances and Applications, vol. 111, 
  XXIII+435, Birkh√§user, 2000.
\item \href{http://www.mai.liu.se/~vlmaz/books/op-coef.html}
  {Differential Equations with Operator Coefficients} (with V. 
  Kozlov), Springer Monographs in Mathematics, Springer-Verlag, 1999.
\item \href{http://www.mai.liu.se/~vlmaz/books/multistr.html}
   {Asymptotic Analysis of Fields in Multistructures} (with V. 
  Kozlov and A. Movchan), Oxford Science Publications, 1999
\item \href{http://www.mai.liu.se/~vlmaz/books/hadamard.html}
           {Jacques Hadamard, a Universal Mathematician}  (with T. 
  Shaposhnikova), American Mathematical Society and London Mathematical 
  Society, 1998.
\item \href{http://www.mai.liu.se/~vlmaz/books/pobor.html}
           {Differentiable Functions on Bad Domains} 
       (with S. Poborchi), World Scientific, 1997.
     \item \href{http://www.mai.liu.se/~vlmaz/books/notes.html}
                {Theory of a Higher-order Sturm-Liouville Equation} 
       (with V.  Kozlov), Springer-Verlag, Lecture Notes in Mathematics, 1997.
     \item \href{http://www.mai.liu.se/~vlmaz/books/elliptic.html}
                {Elliptic Boundary Value Problems in Domains with Point Singularities} 
       (with V. Kozlov and J. Rossman), American Mathematical Society, 1997.
     \item \href{http://www.mai.liu.se/~vlmaz/books/rand2/index.html}
       {Asymptotische Theorie Elliptischer Randwertaufgaben in Singul\" ar Gest\" orten Gebieten II}   
       (with S. Nazarov and B. Plamenevskii), Berlin, 
  Akademie Verlag, Bd.2, 1992.
     \item \href{http://www.mai.liu.se/~vlmaz/books/rand1/index.html}
       {Asymptotische Theorie Elliptischer Randwertaufgaben in Singul\" ar Gest\" orten Gebieten I}   
       (with S. Nazarov and B. Plamenevskii), Berlin, 
  Akademie Verlag, 1991.
\item \href{http://www.mai.liu.se/~vlmaz/books/problems.html}
  {Elliptic Boundary Value Problems}  (with N. Morozov, B. 
  Plamenevskii, L. Stupyalis), American Mathematical Society 
  Translations, Ser. 2, Vol. 123, 1984, AMS.
    \item Encyclopaedia of Mathematical Sciences, Vol. 27, Analysis IV, 
  Linear and Boundary Integral Equations, V.G. Maz'ya, S.M. Nikol'skii 
  (Eds.), Contributors: V.G. Maz'ya, S. Pr\" ossdorf, 233 pages, 
  Springer-Verlag, 1991, V. G. Maz'ya: 
  \href{http://www.mai.liu.se/~vlmaz/books/analysis-III.html}
       {Boundary Integral Equations}, pp.  127--222.
    \item Encyclopaedia of Mathematical Sciences, Vol. 26, Analysis III, 
  Spaces of Differentiable Functions , S.M. Nikol'skii (Ed.), 
  Contributors: L.D. Kudryavtsev, V.G. Maz'ya, S.M. Nikol'skii, 218 
  pages, Springer-Verlag, 1990, V.G. Maz'ya: 
  \href{http://www.mai.liu.se/~vlmaz/books/analysis-III.html}
       {Classes of Domains, Measures and Capacities in the Theory of Differentiable Functions}, 
  pp. 141--211.
\item  \href{http://www.mai.liu.se/~vlmaz/books/mult.html}
            {Theory of Multipliers in Spaces of Differentiable Functions} 
  (with T. Shaposhnikova), Pitman, 1985 (Russian version: Leningrad 
  University Press, 1986).
\item   \href{http://www.mai.liu.se/~vlmaz/books/sobolev.html}{Sobolev Spaces}, 
      Springer-Verlag, 1985 (Russian version: 
  Leningrad University Press, 1985).
\item \href{http://www.mai.liu.se/~vlmaz/books/abschatz.html}
           {Absch\" atzungen fur Differentialoperatoren in Halbraum} 
       (with I.  Gelman), Berlin, Akademie Verlag, 1981; Birkh\" auser, 1982.
     \item \href{http://www.mai.liu.se/~vlmaz/books/teubner-38.html}
                {Zur Theorie Sobolewsche R\" aume}, 
         Series: TEUBNER-TEXTE zur Mathematik
         BSB B. G. Teubner Verlagsgesellschaft, Leipzig, 1981.
       \item \href{http://www.mai.liu.se/~vlmaz/books/teubner-2.html}
                  {Einbettungss\" atze f\" ur Sobolewsche R\" aume}, 
      Teil 2, Series: TEUBNER-TEXTE zur Mathematik, Band 28,
         BSB B. G. Teubner Verlagsgesellschaft, Leipzig, 1980.
   \item \href{http://www.mai.liu.se/~vlmaz/books/teubner-1.html}
                  {Einbettungss\" atze f\" ur Sobolewsche R\" aume}, 
     Teil 1, Series: TEUBNER-TEXTE zur Mathematik
         BSB B. G. Teubner Verlagsgesellschaft, Leipzig, 1979.
       \item \href{http://www.mai.liu.se/~vlmaz/books/burago.html}
         {Potential Theory and Function Theory for Irregular Regions}
  (with Yu. Burago) Seminars in Mathematics, Steklov Institute, 
  Leningrad, Vol. 3, Consultants Bureau, New York, 1969 (Russian 
  version: 1967).
\end{itemize}

  About 480 research papers published.

\end{document} 
