\documentclass{article}
\usepackage[utf8]{inputenc}
%%% --instead of \usepackage{fullpage}
\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep
\textheight 8.9in
\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in
\textwidth 6.5in
% --

\usepackage{amssymb}




\newcommand{\authors}[1]{\item #1\ignorespaces}
\renewcommand{\title}[1]{, \textit{#1}\ignorespaces}
\newcommand{\journal}[1]{, {#1}\ignorespaces}
\newcommand{\book}[1]{, {#1}\ignorespaces}
\newcommand{\series}[1]{, {#1}\ignorespaces}
\newcommand{\publisher}[1]{, {#1}\ignorespaces}
\newcommand{\conference}[1]{, {#1}\ignorespaces}
\newcommand{\volume}[1]{, \textbf{#1}\ignorespaces}
\newcommand{\no}[1]{, no.~{#1}\ignorespaces}
\newcommand{\Year}[1]{, #1\ignorespaces}
\newcommand{\pages}[1]{, pp #1\ignorespaces}
\newcommand{\jitem}[1]{.}
\newcommand{\oitem}[1]{.}
\newcommand{\bitem}[1]{.}
\newcommand{\citem}[1]{.}
\newcommand{\visitor}[1]{#1}
\newcommand{\affiliation}[1]{, #1}
\newcommand{\period}[1]{, #1}



\begin{document}


\begin{center}

\textbf{\Large Publications of Vladimir Maz'ya}

\end{center}





\textbf{\Large Books}

\begin{enumerate}
\item Burago, Yu. D.; Maz'ya, V. G. {\it Certain Questions of
Potential
Theory and Function Theory for Regions
with Irregular Boundaries}. (Russian) Zap. Nau\v cn. Sem. Leningrad.
Otdel.
Mat. Inst. Steklov. (LOMI) {\bf 3} 1967 152 pp;
English translation:  Potential Theory and Function Theory for
Irregular
Regions. Translated from
Russian. Seminars in Mathematics, V. A. Steklov Mathematical
Institute,
Leningrad, Vol. 3 Consultants Bureau, New York 1969 vii+68 pp.

\item Mazja, W. {\it Einbettungss{\"a}tze f\"ur Sobolewsche
R{\"a}ume}.
Teil 1. (German) [Imbedding Theorems for Sobolev Spaces. Part 1]
Translated
from the Russian by J. Nagel. With English, French and Russian
summaries.
Teubner-Texte zur Mathematik. [Teubner Texts on
Mathematics] BSB B. G. Teubner Verlagsgesellschaft, Leipzig, 1979. 204
pp.;
{\it Einbettungss{\"a}tze f\"ur Sobolewsche R{\"a}ume}.
Teil 2. (German) [Imbedding Theorems for
Sobolev Spaces. Part 2] With English, French and Russian summaries.
Teubner-Texte zur Mathematik [Teubner Texts in Mathematics],
28. BSB B. G. Teubner Verlagsgesellschaft, Leipzig, 1980. 188 pp.

\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Asymptotic Behavior of Solutions of
Elliptic Boundary Value Problems under Singular Perturbations of the
Domain}. (Russian) With Georgian and English summaries. Tbilis.
Gos. Univ., Inst. Prikl. Mat., Tbilisi, 1981. 207 pp.

\item Gelman, I. W.; Mazja, W. G. {\it Absch{\"a}tzungen f\"ur
Differentialoperatoren im Halbraum}.
(German) [Estimates for differential operators in the half-space]
Translated from the Russian by Ehrhard Herbst and Werner
Plischke. Edited by G. Wildenhain. Mathematische Lehrb\"ucher und
Monographien, II. Abteilung: Mathematische Monographien
[Mathematical Textbooks and Monographs, Part II: Mathematical
Monographs],
54. Akademie-Verlag, Berlin, 1981. 221 pp.;
Birkh{\"a}user Verlag, Basel-Boston, Mass., 1982.
\item Mazja, W. {\it Zur Theorie Sobolewscher R{\"a}ume}. (German) [On
the
theory of Sobolev spaces] Translated from
the Russian by J. Nagel. With English, French and Russian summaries.
Teubner-Texte zur Mathematik [Teubner Texts in
Mathematics], 38. BSB B. G. Teubner Verlagsgesellschaft, Leipzig,
1981. 170
pp.
\item Maz'ya, V. G.; Morozov, N. F.; Plamenevskii; B. A.; Stupialis,
L.,{\it  Elliptic Boundary Value Problems}, Amer. Math. Soc.
Transl. (1984), {\bf 123}, Ser. 2, 268 pp.

\item Maz'ya, V. G. {\it Sobolev Spaces}. (Russian) Leningrad. Univ.,
Leningrad, 1985. 416 pp.; English translation from the Russian by T.
O.
Shaposhnikova. Springer-Verlag, Berlin-New York, 1985.
xix+486 pp.

\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Theory of Multipliers
in
Spaces of Differentiable Function}.
Monographs and Studies in Mathematics, 23. Pitman, Boston,
Mass.-London,
1985. xiii+344 pp.;
Russian edition by Leningrad. Univ., Leningrad, 1986. 404 pp.

\item Mazja, W. G.; Nasarow, S. A.; Plamenewski, B. A. {\it
Asymptotische
Theorie elliptischer Randwertaufgaben
in singul{\"a}r gest\"orten Gebieten}. I. (German) [Asymptotic theory
of
elliptic boundary value problems in singularly perturbed
domains. I.] {\it St\"orungen isolierter Randsingularit{\"a}ten}.
[Perturbations of isolated boundary singularities] Mathematische
Lehrb\"ucher und Monographien, II. Abteilung: Mathematische
Monographien
[Mathematical Textbooks and Monographs, Part II:
Mathematical Monographs], 82. Akademie-Verlag, Berlin, 1991. 432 pp.;
  II. (German) [Asymptotic theory of elliptic boundary value problems
in
singularly perturbed domains. II]
Nichtlokale St\"orungen. [Nonlocal perturbations] Mathematische
Lehrb\"ucher und Monographien, II. Abteilung: Mathematische
Monographien [Mathematical Textbooks and Monographs, Part II:
Mathematical
Monographs], 83. Akademie-Verlag, Berlin, 1991. 319 pp.

\item Kozlov, V.; Maz'ya, V., {\it Theory of a Higher-order
Sturm-Liouville
Equation}. Lecture Notes
in Mathematics, 1659. Springer-Verlag, Berlin, 1997. xii+140 pp.

\item Kozlov, V. A.; Maz'ya, V. G.; Rossmann, J. {\it Elliptic
Boundary Value Problems in Domains with Point Singularities}.
Mathematical
Surveys and Monographs, 52. American Mathematical
Society, Providence, RI, 1997, x+414 pp.

\item Maz'ya, V.; Poborchi, S. {\it Differentiable Functions on Bad
Domains}. World Scientific, 1997, XVIII+481 pp.

\item Maz'ya, V.; Shaposhnikova, T. {\it Jacques Hadamard, a Universal
Mathematician}. History of Mathematics, 14. American Mathematical
Society,
Providence, RI; London Mathematical Society, London, 1998. xxviii+574
pp.

\item Kozlov, V.;  Maz'ya, V. {\it  Differential Equations with
Operator
Coefficients}. Springer-Verlag, 1999, XV+441.

\item Kozlov, V.; Maz'ya, V.; A. Movchan, A. {\it Asymptotic Analysis
of
Fields in Multistructures}. Oxford Science Publications, 1999.

\item Maz'ya, V.; Nazarov, S.; Plamenevskij, B.,
Asymptotic Theory of Elliptic Boundary Value
Problems in Singularly Perturbed Domains, vol. 1-2, Operator Theory.
dvances and
Applications, vol. 111, XXIII+435 and vol. 112, XXIII+323,
Birkh\"auser, 2000.

\item Kozlov, V. A.; Maz'ya, V. G.; Rossmann, J.,
   {\it Spectral Problems Associated with
     Corner Singularities of Solutions to Elliptic Equations}.
     Mathematical Surveys and
       Monographs, vol.~85, 436 pp., American Mathematical Society,
2000.

\item Kuznetsov, N.; Maz'ya, V.; Vainberg, B. {\it Linear
Water Waves. A Mathematical Approach}. Cambridge University
Press, 2002.

\item Maz'ya, V., Shaposhnikova, T., 
{\it Jacques Hadamard, un Math\'ematicien Universel}. EDP Sciences, Paris, 2005 
(revised and extended translation from English).

\item Kresin, G., Maz'ya, V. 
{\it Sharp Real-Part Theorems. A Unified approach}, Lecture Notes in Mathematics, No 1903, xvi+140 pp, Springer, 2007.

\item Maz'ya, V., Poborchi, S. 
{\it Imbedding and Extension Theorems for Functions in Non-Lipschitz Domains}, St-Petersburg University Publishers, 2007.


\item Maz'ya, V., Schmidt, G., {\it Approximate Approximations}, Mathematical Surveys and Monographs, vol. 141,  xiv+349 pp, American Mathematical Society, 2007.

\item Maz'ya V., Shaposhnikova T., {\it Jacques Hadamard, Legend of  Mathematics}. MCNMO Publishers, Moscow, 2008 (revised,  extended, and  authorized translation from English to Russian).



\item Maz'ya V., Shaposhnikova T., {\it Theory of Sobolev Multipliers with Applications to Differential and Integral Operators}, Grundlehren der Mathematischen Wissenschaften, vol. 337, Springer, 2009.

\item Maz'ya V.,  Soloviev, A., {\it Boundary Integral Equations on Contours with Peaks}, Operator Theory Advances and Applications, vol. 196, Birkh\"auser, 2010.

\item Maz'ya V., Rossmann, J., {\it Elliptic Equations in Polyhedral Domains},      Mathematical Surveys and
       Monographs, vol.~162, 608 pp., American Mathematical Society,
2010.

\item Maz'ya V., {\it Sobolev Spaces with Applications to Elliptic Partial Differential Equations}, Grundlehren der Mathematischen Wissenschaften, vol. 342, Springer, 2011.

\item Kresin, G., Maz'ya, V. {\it Maximum Principles and Sharp Constants for Solutions of Elliptic and Parabolic Systems}, vol. 183, 328 pp., American Mathematical Society,
2012.

\item  Maz'ya, V.,  Movchan, A.,   Nieves, M.  
{\it Green's Kernels and Meso-Scale Approximations in Perforated Domains}, Springer, Lecture Notes in Mathematics,  v. 2077, 2013.

\item Cialdea, A., Maz'ya, V. {\it Semi-bounded Differential Operators, Contractive Semigroups and Beyond}, Operator Theory, Advanves and Applications, vol. 243, Birkh\"auser, 2014


\vfill\eject
\textbf{\Large Papers}

\vspace{1em}
{\bf 1959}
\item Maz'ya, V. G. {\it Solution of Dirichlet's problem for an
equation
of elliptic type}. (Russian) Dokl. Akad.
Nauk SSSR {\bf 129}, 257--260.\hfill\break

{\bf 1960}
\item Maz'ya, V. G. {\it Classes of domains and imbedding theorems for
function spaces}. Soviet Math. Dokl. {\bf 133}:1,
882--885.\hfill\break

{\bf 1961}
\item Maz'ya, V. G. {\it Some estimates of solutions of second-order
elliptic equations}. (Russian) Dokl. Akad. Nauk
SSSR {\bf 137}, 1057--1059.
\item Maz'ya, V. G. {\it On $p$-conductivity and theorems on embedding
certain functional spaces into a $C$-space}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 140}, 299--302.\hfill\break

{\bf 1962}
\item Maz'ya, V. G. {\it The negative spectrum of the
higher-dimensional
Schr\"odinger operator}. (Russian) Dokl. Akad. Nauk
SSSR {\bf 144}, 721--722.
\item Maz'ya, V. G. {\it On the solvability of the Neumann problem}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 147},
294--296.
\item Burago, Yu. D.; Maz'ya, V. G.; Sapo\v znikova, V. D. {\it On the
double layer potential  for non-regular
domains}. (Russian) Dokl. Akad. Nauk SSSR {\bf 147}, 523--525.
\item Maz'ya, V. G.; Sobolevski{\u\i}, P. E. {\it On generating
operators
of semi-groups}. (Russian) Uspehi Mat.
Nauk {\bf 17}:6 (108), 151--154.
\item Maz'ya, V. G. {\it Imbedding theorems for arbitrary sets}.
(Russian)
Uspehi Mat. Nauk {\bf 17}:1, 247-248.\hfill\break

{\bf 1963}
\item Maz'ya, V. G. {\it The Dirichlet problem for elliptic equations
of
arbitrary order in unbounded domains}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 150}, 1221--1224.
\item Maz'ya, V. G. {\it On the boundary regularity of solutions of
elliptic equations and of a conformal mapping}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 152}, 1297--1300.
%\item Maz'ya, V. G. {\it On the maximum principle for a class of
operators
%in Banach space}. (Russian) Vestnik
%Leningrad. Univ. Ser. Mat. Meh. Astronom {\bf 18}:1,
%64--69.\hfill\break

{\bf 1964}
\item Maz'ya, V. G.; Sapo\v znikova, V. D. {\it A remark on the
regularization of a singular system in the isotropic
theory of elasticity}. (Russian) Vestnik Leningrad. Univ. Ser. Mat.
Meh.
Astronom. {\bf 19}:2, 165--167. Erratum in: Vestnik
Leningrad. Univ. Ser. Mat. Meh. Astronom. {\bf 9}:4 (1977), 160.
\item Maz'ya, V. G. {\it On the theory of the higher-dimensional
Schr\"odinger operator}.
(Russian) Izv. Akad. Nauk SSSR Ser. Mat. {\bf 28}, 1145--1172.
\item Maz'ya, V. G. {\it The solvability in $\stackrel{\circ}{W}
\!\!{}^2_2$ of the Dirichlet problem for a region with a smooth
irregular
boundary}. (Russian) Vestnik Leningrad. Univ. {\bf 19}:7 163--165.
\item Maz'ya, V. G.; Sapo\v znikova, V. D. {\it Solution of the
Dirichlet
and Neumann problems for irregular domains by potential-theoretic
methods}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 159}, 1221--1223.\hfill\break

{\bf 1965}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it On singular
equations
with a vanishing symbol}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 160}, 1250--1253.
\item Maz'ya, V. G. {\it Polyharmonic capacity in the theory of the
first
boundary-value problem}.
(Russian) Sibirsk. Mat. \v Z. {\bf 6}, 127--148.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The Cauchy problem
for
hyperbolic singular integral equations
of convolution type}. (Russian) Vestnik Leningrad. Univ. {\bf 20}:19,
61--163.
\item Maz'ya, V. G. {\it On the theory of the multi-dimensional
Schr\"odinger operator}. (Russian) Vestnik Leningrad.
Univ. {\bf 20}:1, 135--137.\hfill\break

{\bf 1966}
\item Maz'ya, V. G. {\it On the modulus of continuity of a solution of
the
Dirichlet problem near an
irregular boundary}.  (Russian) 1966 Problems Math. Anal. Boundary
Value
Problems Integr. Equations (Russian) pp. 45--58 Izdat.
Leningrad. Univ., Leningrad.
\item Burago, Ju. D.; Maz'ya, V. G.; Sapo\v znikova, V. D. {\it On the
theory of potentials of a double and a simple
layer for regions with irregular boundaries}. (Russian) 1966 Problems
Math.
Anal. Boundary Value Problems Integr. Equations
(Russian) 3--34 Izdat. Leningrad. Univ., Leningrad.
\item Mazz'ja, V. G. {\it Boundary value problems in domains with
irregular
boundaries}. Reports of the Internat. Congress of Math.,
Section 7, Moscow, 1966, 42.\hfill\break

{\bf 1967}
\item Maz'ya, V. G. {\it Solvability in
$\stackrel{\circ}{W}\!\!{}^2_2$ of
the Dirichlet problem in a region with a smooth irregular boundary}.
(Russian) Vestnik Leningrad. Univ. {\bf 22}:7, 87--95.
\item Maz'ya, V. G.; Mihlin, S. G. {\it The Cosserat spectrum of the
equations of elasticity theory}.
(Russian) Vestnik Leningrad. Univ. {\bf 22}:13, 58--63.
\item Maz'ya, V. G. {\it The behavior near the boundary of the
solution of
the Dirichlet problem for an
elliptic equation of the second order in divergence form}. (Russian)
Mat.
Zametki {\bf 2}, 209--220.
\item Maz'ya, V. G.; Havin, V. P. {\it Approximation in the mean by
harmonic functions}.
(Russian) Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst. Steklov.
(LOMI)
{\bf 5}, 196--200.
\item Ver\v zbinski{\u\i}, G. M.; Maz'ya, V. G. {\it The asymptotics
of
solutions of the Dirichlet problem
near a non-regular frontier}. (Russian) Dokl. Akad. Nauk SSSR {\bf
176},
498--501.
\item Maz'ya, V. G. {\it Closure in the metric of the generalized
Dirichlet
integral}. (Russian) Zap. Nau\v cn. Sem.
Leningrad. Otdel. Mat. Inst. Steklov. (LOMI){\bf 5}
192--195.\hfill\break

{\bf 1968}
\item Babi\v c, V. M.; Bakel'man, I. Ja.; Ko\v selev, A. I.; Maz'ya,
V. G.
{\it Solomon Grigor'evi\v c Mihlin: On the
sixtieth anniversary of his birth}. (Russian) Uspehi Mat. Nauk {\bf
23}:4
(142), 269--272.
%\item Babi\v c, V. M.; Bakel'man, I. Ya.; Ko\v selev, A. I.; Maz'ya,
%V. G.
%{\it Vladimir Ivanovich Smirnov (on his eightieth birthday)} Russ. Math. Surv. 
% {\bf 24}:4, 181--199.
\item Maz'ya, V. G.; Havin, V. P. {\it Approximation in the mean by
analytic functions}. (Russian) Vestnik
Leningrad. Univ. {\bf 23}:13, 62--74.
\item Maz'ya, V. G.; Havin, V. P. {\it The Cauchy problem for
Laplace's
equation}. (Russian) Vestnik Leningrad.
Univ. {\bf 23}:7, 146--147.
\item Maz'ya, V. G. {\it Examples of nonregular solutions of
quasilinear
elliptic equations with analytic coefficients}.
(Russian) Funkcional. Anal. i Prilo\v zen. {\bf 2}:3, 53--57.
\item Maz'ya, V. G. {\it The Neumann problem in regions with
nonregular
boundaries}. (Russian) Sibirsk.
Mat. \v Z. {\bf 9}, 1322--1350.\hfill\break

{\bf 1969}
\item Maz'ya, V. G. {\it The boundedness of the first derivatives of
the
solution of the Dirichlet problem in a region with smooth
nonregular boundary}. (Russian) Vestnik Leningrad. Univ. {\bf 24}:1,
72--79.
\item Maz'ya, V. G.; Panejah, B. P. {\it Degenerate elliptic
pseudo-differential operators on a smooth manifold
without boundary}. (Russian) Funkcional. Anal. i Prilo\v zen. {\bf
3}:2,
91--92.
\item Maz'ya, V. G. {\it Weak solutions of the Dirichlet and Neumann
problems}. (Russian) Trudy Moskov. Mat. Ob\v s\v c. {\bf 20},
137--172.
\item Maz'ya, V. G.; Havin, V. P. {\it On the uniqueness theorem of L.
Carleson for analytic functions with
finite Dirichlet integral}. (Russian) 1969 Problems of Math. Anal.,
no. 2:
Linear Operators and Operator Equations (Russian) pp.
153--156 Izdat. Leningrad. Univ., Leningrad.
\item Krol', I. N.; Maz'ya, V. G. {\it The lack of continuity and
H\"older
continuity of solutions of a certain
quasilinear equation}. (Russian) Zap. Nau\v cn. Sem. Leningrad. Otdel.
Mat.
Inst. Steklov. (LOMI) {\bf 14} 89--91.
\item Maz'ya, V. G.; Ha{\u\i}kin, Ju. E. {\it A remark on the
continuity in
$L\sb{2}$ of a singular
integral operator}. (Russian) Vestnik Leningrad. Univ. {\bf 24}:19,
156--159.\hfill\break

{\bf 1970}
\item Maz'ya, V. G. {\it The degenerate problem with oblique
derivative}.
(Russian) Uspehi Mat.
Nauk {\bf 25}:2 (152), 275--276.
\item Maz'ya, V. G.; Panejah, B. P. {\it Degenerate elliptic
pseudodifferential operators with simple complex
characteristics}. (Russian) Uspehi Mat. Nauk{\bf 25}:1 (151),
193--194.
\item Maz'ya, V. G.; Havin, V. P. {\it A nonlinear analogue of the
Newtonian potential, and metric
properties of $(p,\,l)$-capacity}. (Russian) Dokl. Akad. Nauk SSSR
{\bf
194}, 770--773.
\item Maz'ya, V. G. {\it The continuity at a boundary point of the
solutions of quasi-linear elliptic equations}.
(Russian) Vestnik Leningrad. Univ. {\bf 25}:13, 42--55; erratum:
Vestnik
Leningrad. Univ. {\bf 27}:1, 160; English
translation: Vestnik Leningrad. Univ. Math. {\bf 3} (1976), 225---242.
\item Maz'ya, V. G., {\it Some questions from the theory of general
differential operators}. In the book: Mikhlin, S. G.
Mathematical physics, an advanced course.  Translated from the
Russian.
North-Holland Series in Applied Mathematics and Mechanics, Vol. 11
North-Holland Publishing Co., Amsterdam-London; American
Elsevier Publishing Co., Inc., New York 1970 xv+561 pp.; German
translation: Maz'ya, W.G. Einige Fragen der Theorie
allgemeiner Differentialoperatoren, In the book: Michlin, S. G.
Lehrgang
der mathematischen Physik. (German)  \"Ubersetzung aus dem
Russischen: Mathematische
Lehrb\"ucher und Monographien. I. Abteilung: Mathematische
Lehrb\"ucher,
Band XV. Akademie-Verlag, Berlin, 1972. xiv+475
pp.
\item Maz'ya, V. G. {\it Classes of sets and measures that are
connected
with imbedding theorems}.
(Russian) Imbedding theorems and their applications (Proc. Sympos.,
Baku,
1966) (Russian), pp. 142--159. Izdat. "Nauka",
Moscow, 1970.
\item Maz'ya, V. G. The selfadjointness of the Laplace operator.
(Russian)
Imbedding theorems and
their applications (Proc. Sympos., Baku, 1966) (Russian), pp.
160--162,
246. Izdat. "Nauka", Moscow, 1970.
\item Maz'ya, V. G.; Panejah, B. P. {\it Coercive estimates and
regularity
of solutions of degenerate elliptic
pseudodifferential equations}. (Russian) Funkcional. Anal. i Prilo\v
zen.
{\bf 4}:4, 41--56.
\hfill\break

{\bf 1971}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The asymptotics of
the
solutions of differential equations with
operator coefficients}. (Russian) Dokl. Akad. Nauk SSSR {\bf 196},
512--515.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The oblique
derivative
problem in a domain with a piecewise
smooth boundary}. (Russian) Funkcional. Anal. i Prilo\v zen {\bf 5}:3,
102--103.
\item Ver\v zbinski{\u\i}, G. M.; Maz'ya, V. G. {\it Asymptotic
behavior of
the solutions of second order elliptic
equations near the boundary}. I. (Russian) Sibirsk. Mat. \v Z. {\bf
12},
1217--1249.\hfill\break

{\bf 1972}
\item Gel'man, I. V.; Maz'ya, V. G. {\it Estimates for differential
operators with constant coefficients
in a half-space}. (Russian) Dokl. Akad. Nauk SSSR {\bf 202}, 751--754.
\item Maz'ya, V. G. {\it The Neumann problem for elliptic operators of
arbitrary order in domains with
nonregular boundaries}. (Russian) Vestnik Leningrad. Univ. no. 1,
26--33.
\item Maz'ya, V. G. {\it The degenerate problem with an oblique
derivativ}.
(Russian) Mat. Sb. (N.S.) {\bf 87} (129),
417--454.
\item Maz'ya, V. G. {\it Applications of certain integral inequalities
to
the theory of quasilinear elliptic equations}.
(Russian) Comment. Math. Univ. Carolinae {\bf 13}, 535--552.
\item Maz'ya, V. G. {\it The removable singularities of bounded
solutions
of quasilinear elliptic equations
of arbitrary order}. (Russian) Boundary value problems of mathematical
physics and related questions in the theory of functions, 6.
Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst. Steklov. (LOMI) {\bf
27},
116--130.
\item Maz'ya, V. G.; Havin, V. P. {\it Approximation in the mean by
harmonic functions}.
(Russian) Investigations on linear operators and the theory of
functions,
III. Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov. (LOMI) {\bf 30}, 91--105.
\item Ver\v zbinski{\u\i}, G. M.; Maz'ya, V. G. {\it Asymptotic
behavior of
the solutions of second
order elliptic equations near the boundary}. II. (Russian) Sibirsk.
Mat. \v
Z. {\bf 13}, 1239--1271.
\item Maz'ya, V. G. {\it On Beurling's theorem on the minimum
principle for
positive harmonic functions}.
(Russian) Investigations on linear operators and the theory of
functions,
III. Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov. (LOMI) {\bf 30}, 76--90.
\item Maz'ya, V. G.; Havin, V. P. {\it On the theory of nonlinear
potentials and $(p,l)$-capacity}. (Russian) Vestnik Leningrad.
Univ. Mat. Meh. Astronom. {\bf 13}:3, 46--51.
\item Maz'ya, V. G. {\it Certain integral inequalities for functions
of
several variables}.
(Russian) Problems of mathematical analysis, no. 3: Integral and
differential operators, Differential equations (Russian), pp.
33--68. Izdat. Leningrad. Univ., Leningrad.
\item Maz'ya, W.G. {\it Einige Fragen der Theorie allgemeiner
Differentialoperatoren}. In the book: Michlin, S. G. Lehrgang der
mathematischen Physik. (German)  \"Ubersetzung aus dem Russischen:
  Mathematische
Lehrb\"ucher und Monographien. I. Abteilung: Mathematische
Lehrb\"ucher,
Band XV. Akademie-Verlag, Berlin, 1972. xiv+475 pp.;
extended version in: Mitteilungen der Math. Gesellschaft der DDR
(1975)
H.1, 92-116.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The asymptotic
behavior
of solutions of differential
equations in Hilbert space}. (Russian) Izv. Akad. Nauk SSSR Ser. Mat.
{\bf
36}, 1080--1133; erratum, ibid. {\bf 37} (1973),
709--710.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A.{\it  A certain class of
manifolds with singularities}.
(Russian) Izv. Vys\v s. U\v cebn. Zaved. Matematika, no. 11(126),
46--52.
\item Krol', I. N.; Maz'ya, V. G. {\it The absence of the continuity
and
H\"older continuity of the solutions of quasilinear elliptic equations
near
a nonregular boundary}. (Russian) Trudy Moskov. Mat. Ob\v s\v c. {\bf
26},
75--94.
\item Va{\u\i}nberg, B. R.; Maz'ya, V. G. {\it Certain stationary
problems
of the linear theory
of surface waves}. (Russian) Dokl. Akad. Nauk SSSR {\bf 205},
310--313.
\item Maz'ya, V. G.; Havin, V. P. {\it A nonlinear potential theory}.
(Russian) Uspehi Mat. Nauk {\bf 27}:6, 67--138.\hfill\break

{\bf 1973}
\item Maz'ya, V. G. {\it A certain embedding operator, and set
functions of
the type of $(p,\,l)$-capacity}.
(Russian) Comment. Math. Univ. Carolinae {\bf 14}, 155--175.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it Elliptic boundary
value
problems with discontinuous
coefficients on manifolds with singularities}. (Russian) Dokl. Akad.
Nauk
SSSR {\bf 210}, 529--532.
\item Maz'ya, V. G. {\it The coercivity of the Dirichlet problem in a
domain with irregular boundary}.
(Russian) Izv. Vys\v s. U\v cebn.
Zaved. Matematika, no. 4(131), 64--76.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The asymptotic
behavior
of solutions of the Navier-Stokes equations near the
edges}. (Russian) Dokl. Akad. Nauk SSSR {\bf 210}, 803--806.
\item Maz'ya, V. G. {\it The oblique derivative problem in a domain
with
edges of various dimensions}.
(Russian) Vestnik Leningrad. Univ. {\bf 7} Mat. Meh. Astronom. Vyp. 2
(1973), 34--39.
\item Maz'ya, V. G. {\it The $(p,\,l)$-capacity, imbedding theorems
and the
spectrum of a selfadjoint
elliptic operator}. (Russian) Izv. Akad. Nauk SSSR Ser. Mat. {\bf 37},
356--385.
\item Maz'ya, V. G. {\it The continuity and boundedness of functions
in S.
L. Sobolev spaces}.
(Russian) Problems of mathematical analysis, no. 4: Integral and
differential operators, Differential equations , pp.
46--77. Izdat. Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; Havin, V. P.{\it  Application of the
$(p,\,l)$-capacity to certain problems of the
theory of exceptional sets}. (Russian) Mat. Sb. (N.S.) {\bf 90} (132)
(1973), 558--591.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. P. {\it The behavior of the
solutions of quasilinear elliptic boundary
value problems in the
neighborhood of a conical point}. (Russian) Boundary value problems of
mathematical physics and related questions in the theory of
functions, 7. Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov.
(LOMI) {\bf 38}, 94--97.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A.{\it  Elliptic boundary
value
problems in a domain with a piecewise smooth
boundary}. (Russian) Proceedings of the Symposium on Continuum
Mechanics
and Related Problems of Analysis (Tbilisi, 1971), Vol. 1
, pp. 171--181. Izdat. "Mecniereba", Tbilisi.
\item Maz'ya, V. G. {\it The degenerate oblique derivative problem}.
(Russian) Proceedings of the Symposium on
Continuum Mechanics and
Related Problems of Analysis (Tbilisi, 1971), Vol. 1 (Russian), pp.
165--170. Izdat. "Mecniereba", Tbilisi.
\item Va{\u\i}nberg, B. R.; Maz'ya, V. G. {\it On the plane problem of
the
motion of a solid
immersed in a fluid}. Trudy Moskov. Mat. Ob\v s\v c. {\bf 28}, 35--56.
\item Va{\u\i}nberg, B. R.; Maz'ya, V. G. {\it On the problem of the
steady
oscillations of a layer of fluid of variable depth}.
(Russian) Trudy Moskov. Mat. Ob\v s\v c. {\bf 28}, 57--74.\hfill\break

{\bf 1974}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The fundamental
solutions of elliptic boundary value problems,
and the Miranda-Agmon maximum principle in domains with conical
points}.
(Russian) Sakharth. SSSR Mecn. Akad. Moambe {\bf 73},
277--280.
\item Gel'man, I. V.; Maz'ya, V. G. {\it Estimates on the boundary for
differential operators with constant
coefficients in a
half-space}. (Russian) Izv. Akad. Nauk SSSR Ser. Mat. {\bf 38},
663--720.
\item Kuznecov, N. G.; Maz'ya, V. G. {\it On the problem of the
steady-state oscillations of a layer of fluid in the presence of an
obstacle}. (Russian) Dokl. Akad. Nauk SSSR {\bf 216}, 759--762.
\item Ver\v zbinski{\u\i}, G. M.; Maz'ya, V. G. {\it The closure in
$L\sb{p}$ of the operator of the
Dirichlet problem in a domain with conical points}. (Russian) Izv.
Vys\v s.
U\v cebn. Zaved. Matematika, no. 6(145), 8-19.
\item Maz'ya, V. G. {\it The connection between two forms of
capacity}.
(Russian) Vestnik Leningrad. Univ. Mat. Mech. Astronom.
{\bf 7}:2, 33--40.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The coefficients in
the
asymptotic expansion of the
solutions of elliptic boundary value problems to near conical points}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 219}, 286--289.
\item Maz'ya, V. G.; Paneyah, B. {\it Degenerate elliptic
pseudo-differential operators and the problem with oblique
derivative}.
(Russian) Collection of articles dedicated to the memory of Ivan
Georgievi\v c Petrovski{\u\i}. Trudy Moskov. Mat. Ob\v s\v c.
{\bf 31}, 237--295.
\item Maz'ya, V. G.; Havin, V. P. {\it The solutions of the Cauchy
problem
for the Laplace equation
(uniqueness, normality, approximation)}. (Russian) Trudy Moskov. Mat.
Ob\v
s\v c. {\bf 30}, 61--114.\hfill\break

{\bf 1975}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it Boundary value
problems
for a second order elliptic equation in a
domain with ribs}.
(Russian) Collection of articles dedicated to the memory of
Academician V.
I. Smirnov. Vestnik Leningrad. Univ. Mat.
Meh. Astronom. {\bf 1}:1, 102--108.
\item Gel'man, I. V.; Maz'ya, V. G. {\it The domination of
differential
operators with constant coefficients in a half-space}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 221}:3, 528--531.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A.
   {\it The coefficients in the asymptotic expansion of the solutions
of
elliptic boundary value problems in a cone}. (Russian) Boundary value
problems of mathematical physics and related questions of the theory
of
functions, 8. Zap. Nau\v cn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov.
(LOMI) {\bf 52}, 110--127.
\item Maz'ya, V. G. {\it The index of closure of the operator of the
Dirichlet problem in a domain with a
nonregular boundary}. (Russian) Problems of mathematical analysis, no.
5:
Linear and nonlinear differential equations, Differential
operators, pp. 98--121. Izdat. Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; Gel'man, I. V. {\it Estimates for differential
operators with constant coefficients in a
half-space}. (Russian) Mat. Sb. (N.S.) {\bf 96} (138), 240--275.
\item Maz'ya, V. G. {\it The summability of functions belonging to
Sobolev
spaces}. (Russian) Problems of
mathematical analysis, no. 5: Linear and nonlinear differential
equations,
Differential operators, pp. 66--98. Izdat.
Leningrad. Univ., Leningrad.
\item Maz'ya, V. G. {\it Einige Richtungen und Probleme der Theorie
elliptischer Gleichungen}. Mitteilungen Gesellschaft der DDR,
H. 1, 26-91.
\item Maz'ya, W.G. {\it Einige Fragen der Theorie allgemeiner
Differentialoperatoren}. Mitteilungen der Math. Gesellschaft der DDR,
H.1, 92-116.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it $L\sb{p}$
estimates, and
the asymptotic behavior of the solutions of elliptic boundary value
problems
in domains with edges}. (Russian) Conference on Differential Equations
and
Applications (Ruse, 1975). Godi\v snik Vis\v s. U\v cebn. Zaved.
Prilo\v zna Mat. {\bf 11}:2, 113--123.

{\bf 1976}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The coefficients in
the
asymptotic expansion of the solutions of
elliptic boundary value problems near an edge}. (Russian) Dokl. Akad.
Nauk
SSSR {\bf 229}:1, 33--36.

\item Maz'ya, V. G.; Ha{\u\i}kin, Ju. E. {\it The continuity of
singular
integral operators in normed spaces}.
(Russian) Vestnik Leningrad. Univ.Mat. Meh. Astronom. {\bf 1}:1,
28--34.


{\bf 1977}
\item Maz'ya, V. G. {\it The connection between Martin's and Euclid's
topologies}. (Russian) Dokl.
Akad. Nauk SSSR {\bf 233}:1, 27--30.
\item Maz'ya, V. G.; Otelbaev, M. {\it Imbedding theorems and the
spectrum
of a certain
pseudodifferential operator}. (Russian) Sibirsk. Mat. \v Z. {\bf
18}:5,
1073--1087.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The asymptotic
behavior
of the solution of the Dirichlet problem
near an isolated singularity on the boundary}. (Russian) Vestnik
Leningrad.
Univ. Mat. Meh. Astronom, {\bf 13}:3,
60--66.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A.; Ha{\u\i}kin, Ju. E.
{\it A
well-posed problem
for singular integral equations with a symbol that goes to zero}.
(Russian)
Differencial'nye Uravnenija {\bf 13}:8,
1479--1486.
\item Fichera, G.; Maz'ya, V. G. {\it In honour of Professor Solomon
G.
Mikhlin on the occasion of his
seventieth birthday}. Applicable Anal. {\bf 7}:3, 167--170.
\item Dudu\v cava, R. V.; Maz'ya, V. G. {\it A uniqueness theorem for
the
integral equation of a thin
  rectangular airfoil}. (Russian) Sakharth. SSR Mecn. Akad. Moambe
{\bf
87}:1, 53--56.
\item Maz'ya, V. G. {\it Strong capacity-estimates for "fractional"
norms}.
(Russian) Numerical methods and
questions on organization of computations. Zap. Nau\v cn. Sem.
Leningrad.
Otdel. Mat. Inst. Steklov. (LOMI) {\bf 70},
161--168.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it Elliptic boundary
value
problems on manifolds with singularities}.
(Russian) Problems in mathematical analysis, no. 6: Spectral theory,
boundary value problems, pp. 85--142. Izdat.
Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The
pseudo-analyticity
of the solutions of elliptic
equations in the space ${\bf R}\sp{n}$}. (Russian) Sakharth. SSR Mecn.
Akad. Moambe {\bf 85}:1, 37--40.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The coefficients in
the
asymptotics of solutions of
elliptic boundary value problems with conical points}. (Russian) Math.
Nachr. {\bf 76}, 29--60.

\item Maz'ya, V. G. {\it Solvability of the problem of oscillations of
a
fluid in the presence of an immersed body}.
(Russian) Boundary value problems of mathematical physics and related
questions in the theory of functions, 10. Zap. Nau\v cn. Sem.
Leningrad. Otdel. Mat. Inst. Steklov. (LOMI) {\bf 69}, 124--128.
\item Maz'ya, V. G. {\it On a stationary problem on small oscillations
of a
fluid in the presence of an imbedded body}.
(Russian) Partial differential equations, 57--79, Proc. Sobolev Sem.,
no.
2, Akad. Nauk SSSR Sibirsk. Otdel., Inst. Mat.,
Novosibirsk.
\item Maz'ya, V. G. {\it Behaviour of solutions to the Dirichlet
problem
for the biharmonic operator at a
boundary point}. Dokl. (Russian) Acad. Nauk USSR {\bf 235}:6,
1263-1266.
\item Maz'ya, V. G. {\it Local square summability of a convolution}.
(Russian) Investigations on linear operators
and the theory of functions, VIII. Zap. Nauchn. Sem. Leningrad. Otdel.
Mat.
Inst. Steklov. (LOMI) {\bf 73}, 211--216. Erratum
in:  Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst. Steklov. (LOMI)
{\bf
113} (1981).\hfill\break


{\bf 1978}
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it Estimates in
$L\sb{p}$
and in H\"older classes, and the
Miranda-Agmon maximum principle for the solutions of elliptic boundary
value problems in domains with singular points on the
boundary}. (Russian) Math. Nachr. {\bf 81}, 25--82.
\item Masja, W.; Nagel, J. {\it \"Uber {\"a}quivalente Normierung der
anisotropen
Funktionalr{\"a}ume $H\sp{\mu }({\bf R}\sp{n})$}. (German)
Beitr{\"a}ge
Anal. no. 12, 7--17.
\item Maz'ya, V. G.; Morozov, N. F.; Plamenevski{\u\i} , B. A. {\it
The
stressed-strained state in a neighborhood
of a crack apex at nonlinear bending of a plate}. (Russian) Dokl.
Akad.
Nauk SSSR {\bf 243}:4, 889--892.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Estimates of the
Green
functions and Schauder estimates of
the solutions of elliptic boundary value problems in a two-sided
corner}.
(Russian) Sibirsk. Mat. Zh. {\bf 19}:5,
1065--1082.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it
$L\sb{p}$-estimates of
solutions of elliptic boundary
value problems in domains with ribs}. (Russian) Trudy Moskov. Mat.
Obshch.
{\bf 37}, 49--93. English translation: Trans. Moscow Math. Soc. {\bf 1} (1980), 49--97.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Schauder estimates
for
the solutions of elliptic boundary
value problems in domains with edges on the boundary}. (Russian)
Partial
differential equations, pp. 69--102, Trudy
Sem. S. L. Soboleva, no. 2, Akad. Nauk SSSR Sibirsk. Otdel., Inst.
Mat.,
Novosibirsk.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Weighted spaces
with
inhomogeneous norms, and boundary
value problems in domains with conical points}. (Russian) Elliptische
Differentialgleichungen (Meeting, Rostock, 1977), pp.
161--190, Wilhelm-Pieck-Univ., Rostock.
\item Maz'ya, V. G. {\it An integral inequality}. (Russian) Sem. Inst.
Prikl. Mat. Dokl. no. 12-13, 33--36.
\item Maz'ya, V. G. {\it On regularity of a boundary point for
elliptic
equations}.  (Russian) Zap. Nauchn. Sem. Leningrad.
Otdel. Mat. Inst. Steklov. (LOMI) {\bf 81}, 197--199.
\item Maz'ya, V. G. {\it Multipliers in Sobolev spaces}. (Russian) In
the
book: Application of function theory and functional
analysis methods to problems of mathematical physics. Pjatoe
Sovetso-\v
Cehoslovackoe Sove\v s\v canie, 1976, 181-189;
Novosibirsk.\hfill\break

{\bf 1979}
\item Kresin, G. I.; Maz'ya, V. G. {\it The essential norm of an
operator
of the double-layer potential type
in the space $C\sb{m}$}. (Russian) Dokl. Akad. Nauk SSSR {\bf 246}:2,
272--275.
\item Maz'ya, V. G. {\it Behaviour of solutions to the Dirichlet
problem
for the biharmonic operator at a
boundary point}. Equadiff IV (Proc. Czechoslovak Conf. Differential
Equations and their Applications, Prague, 1977), pp. 250--262,
Lecture Notes in Math., {\bf 703}, Springer, Berlin.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it Multipliers in
spaces of
functions with fractional derivatives}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 244}:5, 1065--1067.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it Traces and
extensions of
the multipliers in the
space $W\sb{p}\sp{l}$}. (Russian) Uspekhi Mat. Nauk {\bf 34}:2 (206),
205--206.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Asymptotic behavior of the solutions of
elliptic boundary value problems in the case of variation of the
domain
near conic points}. (Russian) Dokl. Akad. Nauk SSSR {\bf
249}:1, 94--96.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it Multipliers in S.
L.
Sobolev spaces}.
(Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no. 2, 33--40.
\item Maz'ya, V. G. {\it Summability, with respect to an arbitrary
measure,
of functions from S. L. Sobolev L. N.
Slobodecki{\u\i} spaces}. (Russian) Investigations on linear operators
and
the theory of functions, IX. Zap. Nauchn. Sem. Leningrad.
Otdel. Mat. Inst. Steklov. (LOMI) {\bf 92}, 192--202.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Asymptotic
behavior of
the fundamental solutions of
elliptic boundary value problems in domains with conical points}.
(Russian)
Boundary value problems. Spectral theory, pp.
100--145, Probl. Mat. Anal., 7, Leningrad. Univ., Leningrad.

\item Maz'ya, V. G. {\it A new integral representation of
differentiable
functions and its applications}.
(Russian) Soobshch. Akad. Nauk Gruzin. SSR {\bf 95}:3, 537--540.


\item Maz'ya, V.; Plamenevski{\u\i} , B.; Stupjalis, L. {\it The
three-dimensional problem of the steady-state motion of
a fluid with a free surface}. (Russian) Differentsial'nye Uravneniya i
Primenen.---Trudy Sem. Protsessy Optimal. Upravleniya I
Sektsiya no. 23, 157 pp.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Pseudoanalyticity
of
the solutions of a perturbed polyharmonic
equation in ${\bf R}\sp{n}$}. (Russian) Scattering theory. Theory of
oscillations, pp. 75--91, Probl. Mat. Fiz., {\bf 9},
Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it Multipliers in
spaces of
differentiable functions}.
(Russian) Theory of cubature formulas and the application of
functional
analysis to problems of mathematical physics (Proc. Sem. S.
L. Sobolev, no. 1, 1979) (Russian), pp. 37--90, Trudy Sem. S. L.
Soboleva,
no. 1, 1979, Akad. Nauk SSSR Sibirsk. Otdel., Inst.
Mat., Novosibirsk.
\item Maz'ya, V. G.; Morozov, N. F.; Plamenevski{\u\i} , B. A. {\it
Nonlinear bending of a plate with a crack}.
(Russian) Differential and integral equations. Boundary value
problems, pp.
145--163, Tbilis. Gos. Univ., Tbilisi.
\item Maz'ya, V. G. {\it The spectrum of V. A. Steklov's problem for a
second-order equation with
nonnegative characteristic form}. (Russian) Soobshch. Akad. Nauk
Gruzin.
SSR {\bf 95}:1, 41--44.
\item Maz'ya, V. G.; Gel'man, I. V. {\it Estimates for the maximal
operator
in a half-space}. I.
(Russian) Beitr{\"a}ge Anal. no. 14, 7--24.
%\vfill\eject
\hfill\break

{\bf 1980}
\item Maz'ya, V. G. {\it An integral representation of functions,
satisfying homogeneous
boundary conditions, and its applications}. (Russian) Izv. Vyssh.
Uchebn.
Zaved. Mat. no. 2, 34--44.
\item Va{\u\i}nberg, B. R.; Maz'ya, V. G. {\it A characteristic Cauchy
problem for a hyperbolic equation}.
(Russian) Uspekhi Mat. Nauk {\bf 35}:1 (211), 193--194.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it A problem of the
motion
of a fluid with a free surface
in a faceted vessel}. (Russian) Dokl. Akad. Nauk SSSR {\bf 250}:6,
315--1317.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it On conditions for
the
boundary in the $L\sb{p}$-theory of
elliptic boundary value problems}. (Russian) Dokl. Akad. Nauk SSSR
{\bf
251}:5, 1055--1059.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it On the first
boundary
value problem for the equations of
hydrodynamics in a domain with a piecewise smooth boundary}. (Russian)
Boundary value problems of mathematical physics and related
questions in the theory of functions, 12. Zap. Nauchn. Sem. Leningrad.
Otdel. Mat. Inst. Steklov. (LOMI) {\bf 96}, 179--186.
\item Gel'man, I. V.; Maz'ya, V. G. {\it The domination of
differential
operators with constant coefficients in a half-space}.
(Russian) Math. Nachr. {\bf 95}, 47--78.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it A coercive estimate
for
solutions of elliptic equations
in spaces of multipliers}. (Russian) Vestnik Leningrad. Univ. Mat.
Mekh.
Astronom. no. 1, 41--47.
\item Maz'ya, V. G.; \v Sapo\v snikova, T. O. {\it Theory of
multipliers in
spaces of differentiable functions and
their applications}. (Russian) Theory of cubature formulas and
numerical
mathematics (Proc. Conf., Novosibirsk, 1978), pp.
225--233, "Nauka" Sibirsk. Otdel., Novosibirsk.
\item Maz'ya, V. G. {\it An imbedding theorem and multipliers in pairs
of
S. L. Sobolev spaces}.
(Russian) Theory of analytic functions and harmonic analysis. Akad.
Nauk
Gruzin. SSR Trudy Tbiliss. Mat. Inst. Razmadze {\bf 66},
59--69.
\item Maz'ya, V. G.; Hvoles, A. A. {\it Imbedding of the space
$\stackrel{\circ}{L}\!\!{}_p^l(\Omega )$ into a space of generalized
functions}.  (Russian) Theory of analytic functions and harmonic
analysis.
Akad. Nauk Gruzin. SSR Trudy Tbiliss. Mat. Inst.
Razmadze {\bf 66}, 70--83.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Multipliers of S. L.
Sobolev
spaces in a domain}.
(Russian) Math. Nachr. {\bf 99}, 165--183.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Multipliers in pairs of
spaces of potentials}.
(Russian) Math. Nachr. {\bf 99}, 363--379.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it On the regularity of
the
boundary in the $L\sb{p}$-theory of
elliptic boundary value problems}. I. (Russian) Partial differential
equations, pp. 39--56, Trudy Sem. S. L. Soboleva, no. 2,
Akad. Nauk SSSR Sibirsk. Otdel., Inst. Mat., Novosibirsk.
\item Maz'ya, V. G.; Preobrazhenski{\u\i} , S. P. {\it Some estimates
of
$(l,\,p)$-capacities and their
application to embedding theorems}. (Russian) Soobshch. Akad. Nauk
Gruzin.
SSR {\bf 100}:1, 25--28.
\item Maz'ya, V. G.; Gel'man, I. V. {\it Estimates for the maximal
operator
in a half-space}. II.
(Russian) Beitr{\"a}ge Anal. no. 15, 7--25.
\item Maz'ya, V.; Nazarov, S.; Plamenevski\u \i , B. {\it Asymptotic
behavior of
the solutions of a quasilinear equation in nonregular perturbed
domains}.
(Russian) Differentsial'nye Uravneniya i Primenen.---Trudy
Sem. Protsessy Optimal. Upravleniya I Sektsiya no.{\bf 27},
7--50.\hfill\break

{\bf 1981}
\item Maz'ya, Y. G.; \v Sapo\v snikova, T. O. {\it Multipliers on the
spaces $W\sp{m}\sb{p}$, and their applications}.
(Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no. 1, 42--47.
\item Maz'ya, V. G. {\it On the extension of functions belonging to S.
L.
Sobolev spaces}.
(Russian) Investigations on linear operators and the theory of
functions,
XI. Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov. (LOMI) {\bf 113}, 231--236.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Sufficient conditions
for
belonging to classes of multipliers}.
(Russian) Math. Nachr. {\bf 100}, 151--162.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it On
the
asymptotic behavior of the solutions to the
  Dirichlet problem in a three-dimensional domain with a cut-out thin
body}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 256}1,
37--39.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Multipliers in pairs of
spaces of differentiable functions}.
(Russian) Trudy Moskov. Mat. Obshch. {\bf 43}, 37--80.

\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it Properties of
solutions
of three-dimen\-sional problems of the theory of elasticity and
hydrodynamics in domains with isolated singular points}. (Russian)
Comm.
Math. Phys. {\bf 82}:2, 99--120.

\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Asymptotics of the solutions of the
Dirichlet problem in a domain with an excluded thin tube}. (Russian)
Uspekhi Mat. Nauk {\bf 36}:5 (221), 183--184.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
The
asymptotic behavior of solutions of the Dirichlet
problem in a domain with a cut out thin tube}. (Russian) Mat. Sb.
(N.S.)
{\bf 116}:2, 187--217.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Change of variables as
an
operator on a pair of S. L. Sobolev
spaces}. (Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no.
1,
43--48.
\item Kresin, G. I.; Maz'ya, V. G. {\it On the maximum principle for
Lam\'e
and Stokes systems in a half-space}.
(Russian) Akad. Nauk Armyan. SSR Dokl. {\bf 73}:1, 46--50.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it On the regularity of
the
boundary in the $L\sb{p}$-theory of
elliptic boundary value problems}. II. (Russian) Theory of cubature
formulas and the application of functional analysis to problems
of mathematical physics, pp. 57--102, Trudy Sem. S. L. Soboleva, no.
1,
Akad. Nauk SSSR Sibirsk. Otdel., Inst. Mat.,
Novosibirsk.
\item Va{\u\i}nberg, B. R.; Maz'ya, V. G. {\it The characteristic
Cauchy
problem for a hyperbolic equation}.
(Russian) Trudy Sem. Petrovsk. no. 7, 101--117.
\item Maz'ya, V. G.; Plamenevski{\u\i} , B. A. {\it On the maximum
principle for the biharmonic equation in a
domain with conical points}. (Russian) Izv. Vyssh. Uchebn. Zaved. Mat.
no.
2, 52--59.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it On
the
asymptotic behavior of solutions of
elliptic boundary value problems with irregular perturbations of the
domain}. (Russian)  Probl. Mat. Anal.,
8, pp. 72--153, Leningrad. Univ., Leningrad.
\item Maz'ya, V. G. {\it On the influence of boundary conditions on
imbedding theorems}. (Russian) In the book: Boundary value
problems of mathematical physics, 66-72, Kiev.


\item Kresin, G. I.; Maz'ya, V. G. {\it The essential norm of an
operator
of the double-layer potential type
in the space $C\sb{m}$}. (Russian) Funkzion. Anal. i Vychisl. Matem.
``Nauka'', Alma-Ata, 131-165.\hfill\break

{\bf 1982}
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Homogeneous solutions of the
Dirichlet problem in the exterior of a thin cone}. (Russian) Dokl.
Akad.
Nauk SSSR {\bf 266}:2, 281--284.
\item Maz'ya, V. G. {\it Theory of multipliers in spaces of
differentiable
functions and its applications}. Nonlinear
analysis, function spaces and applications, Vol. 2 (P'{\i}sek, 1982),
pp.
150--190, Teubner-Texte zur Math. {\bf 49}, Teubner,
Leipzig.
\item Kerimov, T. M.; Maz'ya, V. G.; Novruzov, A. A. {\it An analogue
of
Wiener's criterion for the Zaremba problem
in a cylindrical domain}. (Russian) Funktsional. Anal. i Prilozhen.
{\bf
16}:4, 70--71.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Asymptotic behavior of the solution of the Dirichlet
problem in a domain with a thin bridge}. (Russian) Funktsional. Anal.
i
Prilozhen. {\bf 16}:2, 39--46.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Absence
of a De Giorgi-type theorem for
strongly elliptic equations
with complex coefficients}. (Russian) Boundary value problems of
mathematical physics and related questions in the theory of
functions, 14. Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst. Steklov.
(LOMI) {\bf 115}, 156--168.\hfill\break

{\bf 1983}
\item Maz'ya, V. G. {\it Functions with a finite Dirichlet integral in
a
domain with a cusp at the boundary}.
(Russian) Investigations on linear operators and the theory of
functions,
XII. Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov. (LOMI) {\bf 126}, 117--137.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i} , B. A. {\it
Calculation of the asymptotics of "coefficients of intensity"
in the coming together of corner or conic points}. (Russian) Zh.
Vychisl.
Mat. i Mat. Fiz. {\bf 23}:2, 333--346.
\item Zargaryan, S. S.; Maz'ya, V. G. {\it Singularities of solutions
of a
system of equations of potential theory for Zaremba's problem}.
(Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no. 1, 43--48.

\item Maz'ya, V. G.; Donchev, T. {\it Regularity in the sense of
Wiener of
a boundary point for a polyharmonic operator}.
(Russian) C. R. Acad. Bulgare Sci. {\bf 36}:2, 177--179.
\item Maz'ya, V. G.; Shaposhnikova, T. O. {\it Theory of multipliers
in
spaces of differentiable functions}.
(Russian) Uspekhi Mat. Nauk {\bf 38}:3 (231), 23--86.
\item Kresin, G. I.; Maz'ya, V. G. {\it The maximum principle for
second-order elliptic and parabolic systems}.
(Russian) Dokl. Akad. Nauk SSSR {\bf 273}:1, 38--41.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i}, B. A. {\it
Singularities of solutions of the Dirichlet
problem in the exterior of a thin cone}. (Russian) Mat. Sb. (N.S.)
{\bf
122} (164):4, 435--457.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i}, B. A. {\it
Bending
of a near-polygonal plate with a free open boundary}.
(Russian) Izv. Vyssh. Uchebn. Zaved. Mat. no. 8, 34--40.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The first boundary
value
problem for classical equations of mathematical physics
in domains with piecewise-smooth boundaries}. I. (Russian) Z. Anal.
Anwendungen {\bf 2}:4, 335--359.
\item Maz'ya, V. G.; Plamenevski{\u\i}, B. A. {\it The first boundary
value
problem for classical equations of
mathematical physics in domains with piecewise smooth boundaries}. II.
(Russian) Z. Anal. Anwendungen {\bf 2}:6,
523--551.\hfill\break

{\bf 1984}
\item Maz'ya, V. G.; Preobrazenskii, S. P. {\it Estimates for
capacities
and traces of potentials}.
Internat. J. Math. Math. Sci. {\bf 7}:1, 41--63.
\item Maz'ya, V. G. {\it The modulus of continuity of a harmonic
function
at a boundary point}.
(Russian) Investigations on linear operators and the theory of
functions,
XIII. Zap. Nauchn. Sem. Leningrad. Otdel. Mat. Inst.
Steklov. (LOMI) {\bf 135}, 87--95.
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Extension of functions
from
S. L. Sobolev spaces to
the exterior and interior of a small domain}. (Russian) Vestnik
Leningrad.
Univ. Mat. Mekh. Astronom. no. 2, 27--32.
\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i}, B. A. {\it
Asymptotic expansions of eigenvalues of boundary value problems
for the Laplace operator in domains with small openings}. (Russian)
Izv.
Akad. Nauk SSSR Ser. Mat. {\bf 48}:2, 347--371.
\item Maz'ya, V.~G.; Kresin, G.~I. {\it The maximum principle for
second-order strongly elliptic and parabolic systems with constant
coefficients}. (Russian) Mat. Sb. (N.S.) {\bf 125}(167):4, 458--480.

\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i}, B. A. {\it The
Dirichlet problem in domains with thin
cross connections}. (Russian) Sibirsk. Mat. Zh. {\bf 25}:2, 161--179.
\item Zargaryan, S. S.; Maz'ya, V. G. {\it The asymptotic form of the
solutions of integral equations of potential
theory in the neighbourhood of the corner points of a contour}.
(Russian)
Prikl. Mat. Mekh. {\bf 48}:1, 169--174; translation in J.
Appl. Math. Mech. {\bf 48}:1, 120--124 (1985).

\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Extension of functions
belonging to S. L. Sobolev spaces into the exterior of a domain with a
cusp
on the boundary}. (Russian) Dokl. Akad. Nauk SSSR {\bf 275}:5,
1066--1069.


\item Maz'ya, V. G.; Nazarov, S. A.; Plamenevski{\u\i}, B. A. {\it
Elliptic
boundary value problems in domains of the type of the
exterior of a cusp}. (Russian) Linear and nonlinear partial
differential
equations. Spectral asymptotic behavior, 105--148, Probl.
Mat. Anal., {\bf 9}, Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; Nazarov, S. A. {\it On the Sapondjan-Babu\v ska
paradox for problems of the theory of thin plates}.
(Russian) Dokl. Acad. Nauk Arm. SSR {\bf 48}:3, 127-130.
\item Maz'ya, V. G. {\it \"Uber die Regularit\"at eines Randpunktes
f\"ur
elliptisc he Differentialgleichungen}. (German) Linear and
complex analysis problem book, 199 research problems, Lecture Notes in
Math. {\bf 1043}, 507-514.
\item Maz'ya, V. G. Rossman, J. {\it \"Uber die L\"osbarkeit und
Asymptotik
der L\"osungen elliptischer Randwertaufgaben in Gebiten
mit Kanten}. (German) Akad. der Wiss. der DDR, Inst. fur Math. I
Preprint
P-Math. 07/84, s. 1-50; II Preprint P-Math. 30/84, s.
1-50; III Preprint P-Math. 31/84, s. 1-50.\hfill\break

{\bf 1985}
\item Kresin, G. I.; Maz'ya, V. G. {\it On the maximum of
displacements in
a viscoelastic half-space (a three-dimensional model)}.
(Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no. 4, 47--51.
\item Kozlov, V. A.; Maz'ya, V. G.; Parton, V. Z. {\it Asymptotic form
of
the stress intensity coefficients in
quasistatic temperature problems for a domain with a cut}. (Russian)
Prikl.
Mat. Mekh. {\bf 49}:4, 627--636; translation in J.
Appl. Math. Mech. {\bf 49}:4, 482--489 (1986).
\item Gel'man, I. V.; Maz'ya, V. G. {\it Estimates in a half-space for
systems of differential operators
  with constant coefficients}. (Russian) Qualitative analysis of
solutions
of partial differential equations, 70--99,
Akad. Nauk SSSR Sibirsk. Otdel., Inst. Mat., Novosibirsk.
\item Kuznetsov, N. G., Maz'ya, V. G. {\it Asymptotic expansions for
transient surface waves due to short-period oscillating
disturbances}. (Russian) Proc. Leningrad Shipbuild. Inst./ Math.
Modelling
and Automated Design in Shipbuilding, 57-64.\hfill\break

{\bf 1986}
\item Maz'ya, V. G.; Nazarov, S. A. {\it The apex of a cone can be
irregular in Wiener's sense for a fourth-order
elliptic equation}. (Russian) Mat. Zametki {\bf 39}:1, 24--28.
\item Maz'ya, V. G.; Kufner, A. {\it Variations on the theme of the
inequality $(f')\sp 2\leq 2f\,{\rm sup}\,\vert f"\vert $}. Manuscripta
Math. {\bf 56}:1, 89--104.
\item Kuznetsov, N. G.; Maz'ya, V. G. {\it Asymptotic expansions for
surface waves caused by
  short-term disturbances}. (Russian) Asymptotic methods, 103--138,
"Nauka"
Sibirsk. Otdel., Novosibirsk.
\item Kozlov, V. A.; Maz'ya, V. G. {\it Estimates of the $L\sb
p$-means and
asymptotic behavior of the solutions of elliptic
boundary value problems in a cone. I. The case of the model operator}.
(Russian) Seminar Analysis, 55--91, Akad. Wiss. DDR, Berlin.
\item Grachev, N. V.; Maz'ya, V. G. {\it The Fredholm radius of
operators
of double layer potential type on piecewise smooth
surfaces}. (Russian) Vestnik Leningrad. Univ. Mat. Mekh. Astronom. no.
4,
60--64.
\item Maz'ya, V. G. {\it Boundary integral equations of elasticity in
domains with piecewise smooth boundaries}.
Equadiff 6 (Brno, 1985), 235--242, Lecture Notes in Math., {\bf 1192},
Springer, Berlin-New York.
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Extension of functions
in
S. L. Sobolev classes to the
exterior of a domain with the vertex of a peak on the boundary}. I.
(Russian) Czechoslovak Math. J. {\bf 36} (111):4,
634--661.
\item Maz'ya, V. G.; Nazarov, S. A. {\it Paradoxes of the passage to
the
limit in solutions of boundary
value problems for the approximation of smooth domains by polygons}.
(Russian) Izv. Akad. Nauk SSSR Ser. Mat. {\bf 50}:6,
1156--1177.
\item Maz'ya, V. G. {\it On potential theory for the Lam\'e system in
a
domain with a piecewise smooth boundary}.
(Russian) Partial differential equations and their applications
(Tbilisi,
1982), 123--129, Tbilis. Gos. Univ.,
Tbilisi.
\item Maz'ya, V. G., Slutskii, A. S., Fomin, V. A. {\it Asymptotic
behaviour of the stress function near the vertex of a crack in
the problem of torsion under steady-state creep}. (Russian) Mech.
Tverd.
Tela {\bf 4}, 170-176.\hfill\break

{\bf 1987}
\item Maz'ya, V. G.; Sulimov, M. G. {\it Asymptotic behavior of
solutions
of one-dimensional difference equations
with constant operator coefficients}. (Russian) Mat. Sb. (N.S.) {\bf
132}
(174):4, 451--469.
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Extension of functions
in
S. L. Sobolev
classes to the exterior of a domain with the
vertex of a peak on the boundary}. II. (Russian) Czechoslovak Math. J.
{\it
37} (112):1, 128--150.
\item Maz'ya, V. G.; Slutski{\u\i}, A. S. {\it Averaging of
differential
equations on a fine grid}. (Russian) Dokl.
Akad. Nauk SSSR {\bf 293}:4, 792--796.
\item Kozlov, V. A.; Maz'ya, V. G. {\it Singularities of solutions of
the
first boundary value problem for
the heat equation in domains with conical points}. I. (Russian) Izv.
Vyssh.
Uchebn. Zaved. Mat. no. 2, 38--46.
\item Kozlov, V. A.; Maz'ya, V. G. {\it Singularities of solutions of
the
first boundary value problem for the heat
equation in domains with conical points}. II. (Russian) Izv. Vyssh.
Uchebn.
Zaved. Mat. no. 3, 37--44.
\item Maz'ya, V. G.; Nazarov, S. A. {\it Asymptotic behavior of energy
integrals under small
perturbations of the boundary near corner and conic points}. (Russian)
Trudy Moskov. Mat. Obshch. {\bf 50}, 79--129.
\item Maz'ya, V. G.; Slutski{\u\i}, A. S.{\it  Averaging of a
differential
operator on a fine periodic curvilinear net}. (Russian)
Math. Nachr. {\bf 133}, 107--133.
\item Kuznetsov, N. G.; Maz'ya, V. G. {\it Asymptotic expansions for
surface waves
that can be induced by rapidly oscillating or accelerating
perturbations}.
(Russian) Asymptotic methods, 136--175,
"Nauka" Sibirsk. Otdel., Novosibirsk.
\item Maz'ya, V. G.; Slutski{\u\i}, A. S. {\it Averaging of difference
equations with rapidly oscillating coefficients}.
(Russian) Seminar Analysis (Berlin, 1986/87), 63--92, Akad. Wiss. DDR,
erlin.
\item Maz'ya, V. G. {\it A boundary integral equation of the Dirichlet
problem in a plane domain with a cusp at the boundary}.
(Russian) Current problems in mathematical physics, Vol. II (Tbilisi,
1987), 263--270, Tbilis. Gos. Univ.,
Tbilisi.\hfill\break

{\bf 1988}
\item Maz'ya, V. G.; Solov'ev, A. A. {\it Solvability of an integral
equation of the Dirichlet problem in a plane
domain with cusps on the boundary}. (Russian) Dokl. Akad. Nauk SSSR
{\bf
298}:6, 1312--1315; translation in Soviet Math.
Dokl. {\bf 37}:1, 255--258.
\item Maz'ya, V. G. {\it Classes of domains, measures and capacities
in the
theory of spaces of differentiable functions}.
(Russian) Current problems in mathematics. Fundamental directions,
Vol. 26
(Russian), 159--228, Itogi Nauki i Tekhniki, Akad.
Nauk SSSR, Vsesoyuz. Inst. Nauchn. i Tekhn. Inform., Moscow; English
translation: Analysis, III, 141--211, Encyclopaedia
Math. Sci., {\bf 26}, Springer, Berlin, 1991.
\item Maz'ya, V. G. {\it Boundary integral equations}. (Russian)
Current
problems in mathematics. Fundamental
directions, Vol. 27 (Russian), 131--228, Itogi Nauki i Tekhniki, Akad.
Nauk
SSSR, Vsesoyuz. Inst. Nauchn. i Tekhn. Inform.,
Moscow; English translation: Analysis, IV, 127--222, Encyclopaedia
Math.
Sci., {\bf 27},
Springer, Berlin, 1991.
\item Maz'ya, V. G.; Solov'ev, A. A. {\it Asymptotic behavior of the
solution of an integral equation of the
Neumann problem in a plane domain with cusps at the boundary}.
(Russian)
Soobshch. Akad. Nauk Gruzin. SSR {\bf 130}:1,
17--20.
\item Maz'ya, V. G.; Rossmann, J. {\it \"Uber die Asymptotik der
L\"osungen
elliptischer Randwertaufgaben in der
Umgebung von Kanten}. (German) [On the asymptotics of solutions of
elliptic
boundary value problems in the neighborhood of edges]
Math. Nachr. {\bf 138}, 27--53.
\item Kozlov, V. A.; Maz'ya, V. G. {\it Estimates of the $L\sb
p$-means and
asymptotic behavior of the solutions of elliptic boundary value
problems in
a cone}. II. Operators with variable coefficients. (Russian) Math.
Nachr.
{\bf 137}, 113--139.


\item Kozlov, V. A.; Maz'ya, V. G. {\it Spectral properties of
operator
pencils generated by elliptic boundary value problems in a cone}.
(Russian)
Funktsional. Anal. i Prilozhen. {\bf 22}:2, 38--46, 96; translation in
Functional Anal. Appl. {\bf 22}: 2, 114--121.

\item Kerimov, T. M.; Maz'ya, V. G.; Novruzov, A. A. {\it A criterion
for
the regularity of the infinitely
distant point for the Zaremba problem in a half-cylinder}. (Russian)
Z.
Anal. Anwendungen {\bf 7}:2, 113--125.
\item Kresin, G. I.; Maz'ya, V. G. {\it A sharp constant in a
Miranda-Agmon-type inequality for solutions of elliptic
equations}. (Russian) Izv. Vyssh. Uchebn. Zaved. Mat. no. 5, 41--50;
translation in Soviet Math. (Iz. VUZ) {\bf 32}:5,
49--59.
\item Kozlov, V. A.; Maz'ya, V. G.; Parton, V. Z. {\it Thermal shock
in a
region with a crack}.
(Russian) Prikl. Mat. Mekh. {\bf 52}:2, 318--326; translation in J.
Appl.
Math. Mech. {\bf 52}:2, 250--256.
\item Kuznetsov, N. G.; Maz'ya, V. G. {\it Unique solvability of a
plane
stationary problem connected with the motion of a
body submerged in a fluid}. (Russian) Differentsial'nye Uravneniya
{\bf
24}:11, 1928--1940; translation in
Differential Equations {\bf 24}:11, 1291--1301.
\item Kozlov, V. A.; Maz'ya, V. G. {\it An asymptotic formula for
eigenfunctions of the Dirichlet problem in a
domain with a conic point}. (Russian) Vestnik Leningrad. Univ. Mat.
Mekh.
Astronom. no. 4, 30--33,; translation in
Vestnik Leningrad Univ. Math. {\bf 21}:4, 36--40.
\item Grachev, N. V.; Maz'ya, V. G. {\it Representations and estimates
for
inverse operators of integral
equations of potential theory for surfaces with conic points}.
(Russian)
Soobshch. Akad. Nauk Gruzin. SSR {\bf 32}:1,
21--24.
\item Maz'ya, V. G. {\it Inversion formulas for boundary integral
equations
and their applications}.
(Russian) Functional and numerical methods in mathematical physics,
127--131, "Naukova Dumka", Kiev.
\item Maz'ya, V. G., Poborchi{\u\i}, S. V. {\it Traces of functions in
Sobolev spaces on the boundary of a domain with a peak}.
Preprint, MD 87.91, VGM SVP, TR 88-01, University of Maryland.
\item Kuznetsov, N.G.; Maz'ya, V.G. {\it Unique solvability of the
plane
Neumann-Kelvin problem}. (Russian) Mat. Sb. (N.S.) {\bf 135} (177):4,
40--462;
translation in Math. USSR-Sb. 63 (1989), no. 2, 425--446. \hfill\break

{\bf 1989}
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Traces of functions
with a
summable gradient in a domain with a
cusp at the boundary}. (Russian) Mat. Zametki {\bf 45}:1, 57--65, 140;
translation in Math. Notes {\bf 45}:1-2,
39--44.
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Traces of functions
from S.
L. Sobolev spaces on
small and large components of the boundary}. (Russian) Mat. Zametki
{\bf
45}:4, 69--77, 126; translation in Math. Notes
{\bf 45}:3-4, 312--317.
\item Maz'ya, V. G.; Nazarov, S. A. {\it Singularities of solutions of
the
Neumann problem at a
conic point}. (Russian) Sibirsk. Mat. Zh. {\bf 30}:3, 52--63, 218;
translation in Siberian Math. J. {\bf 30}:3,
387--396.
\item Maz'ya, V. G.; Solov'ev, A. A. {\it An integral equation of the
Dirichlet problem in a plane domain with cusps on the
boundary}. (Russian) Mat. Sb. {\bf 180}:9, 1211--1233.
\item Kozlov, V. A.; Maz'ya, V. G.; Parton, V. Z. {\it Thermal shock
in a
thin plate with a crack in the
presence of heat exchange with the surrounding medium}. (Russian) Izv.
Akad. Nauk Armyan. SSR Ser. Mekh. {\bf 42}:2,
41--49.
\item Kresin, G. I.; Maz'ya, V. G. {\it On the maximum modulus
principle
for solutions of linear parabolic systems}.
Seminar Analysis (Berlin, 1988/1989), 41--50, Akad. Wiss. DDR, Berlin.
\item Levin, A. V.; Maz'ya, V. G. {\it Asymptotics of the densities of
harmonic potentials near the apex of a cone}.
(Russian) Z. Anal. Anwendungen {\bf 8}:6, 501--514.
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it Traces of functions in
Sobolev spaces on a boundary of a
domain with a cusp}. (Russian) Trudy Inst. Mat. (Novosibirsk) {\bf
14},
Sovrem. Probl. Geom. Analiz., 182--208; translation in
Siberian Advances in Mathematics {\bf 1}:3 (1991), 75-107.
\item Kozlov, V. A.; Maz'ya, V. G. {\it Iterative procedures for
solving
ill-posed boundary value problems that preserve the
differential equations}. (Russian) Algebra i Analiz {\bf 1}:5,
144--170;
translation in Leningrad Math. J. {\bf 1} (1990), no.
5, 1207--1228.
\item Kozlov, V. A.; Kondrat'ev, V. A.; Maz'ya, V. G. {\it On sign
variability and the absence of "strong" zeros
of solutions of elliptic equations}. (Russian) Izv. Akad. Nauk SSSR
Ser.
Mat. {\bf 53}:2, 328--344; translation in Math.
USSR-Izv. {\bf 34} (1990), no. 2, 337--353.
%\vfill\eject
\hfill\break

{\bf 1990}
\item Grachev, N. V.; Maz'ya, V. G. {\it The Fredholm radius of
integral
operators of potential theory}. (Russian) Nonlinear
equations and variational inequalities. Linear operators and spectral
theory, 109--133, Probl. Mat. Anal., {\bf 11},
Leningrad. Univ., Leningrad.
\item Maz'ya, V. G.; Solov'ev, A. A. {\it On a boundary integral
equation
for the Neumann
problem for a domain with a peak}. (Russian) Trudy Leningrad. Mat.
Obshch.
{\bf 1}, 109--134.
\item Kozlov, V.A.; Levin, A.V.; Maz'ya, V. G. {\it A mathematical
algorithm 
 for reconstruction of the
optic distribution of the power dencity under the
sondage of a laser beam}. Preprint 35, Leningrad Department of the
Institute for Engineering Studies Acad. Nauk SSSR, 1-45.


\item Maz'ya, V. G.; Morozov, N. F.; Nazarov, S. A. {\it On the
elastic
strain energy release due to the variation of the domain
near the angular stress concentrator}. Preprint, LiTH-MAT-R-90-21,
Link\"oping University.
\item Kozlov, V. A.; Maz'ya, V. G.; Parton, V. Z. {\it Some
mathematical
problems of thermoelasticity. Problems of the long-term
strength of power equipment}. Proc. of the Polzunov Central Research
Institute of power equipment, Leningrad, no. 260,
55-67.
\item Maz'ya, V. G.; Tashchiyan, G. M. {\it On the behavior of the
gradient
of the solution of the Dirichlet problem
for the biharmonic equation near a boundary point of a
three-dimensional
domain}. (Russian) Sibirsk. Mat. Zh. {\bf 31}:6,
113--126; translation in Siberian Math. J. {\bf 31}:6, 970--983
(1991).
\hfill\break

{\bf 1991}
\item Kozlov, V. A.; Maz'ya, V. G.; Fomin, A. V. {\it An iterative
method
for solving the Cauchy problem for
elliptic equations}. (Russian) Zh. Vychisl. Mat. i Mat. Fiz. {\bf
31}:1,
64--74.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On stress singularities near
the
boundary of a polygonal crack}.
Proc. Roy. Soc. Edinburgh Sect. A {\bf 117}:1-2, 31--37.
\item Maz'ya, V. G.; Rossmann, J. {\it On the Agmon-Miranda maximum
principle for solutions of
elliptic equations in polyhedral and polygonal domains}. Ann. Global
Anal.
Geom. {\bf 9}:3, 253--303.
\item Grachev, N. V.; Maz'ya, V. G. {\it A contact problem for the
Laplace
equation in the exterior of the boundary
of a dihedral angle}. (Russian) Math. Nachr. {\bf 151}, 207--231.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On the spectrum of an operator
pencil generated by the Dirichlet problem
in a cone}. (Russian) Mat. Sb. {\bf 182}:5, 638--660.
\item Maz'ya, V. G.; Poborchi, S. V. {\it Boundary traces of functions
from
Sobolev spaces on a domain with a cusp}
[translation of Trudy Inst. Mat. (Novosibirsk) {\bf 14} (1989),
Sovrem.
Probl. Geom. Analiz., 182--208; Siberian
Advances in Mathematics {\bf 1} (1991), no. 3, 75--107.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On the spectrum of an operator
pencil generated by the Neumann
problem in a cone}. (Russian) Algebra i Analiz {\bf 3}:2, 111--131;
translation in St. Petersburg Math. J. {\bf 3} (1992), no.
2, 333--353.
\item Grachev, N.; Maz'ya, V. G. {\it Estimates for kernels of the
inverse
operators of the integral equations of elasticity on
surfaces with conic points}. Preprint LiTH-MAT-R-91-07, Link\"oping
niversity.
\item Grachev, N.; Maz'ya, V. G. {\it Invertibility of the boundary
integral operators of elasticity on surfaces with conic points}.
Preprint LiTH-MAT-R-91-08, Link\"oping University.
\item Grachev, N.; Maz'ya, V. G. {\it Estimates for fundamental
solutions
of the Neumann problem in a polyhedron}. Preprint,
LiTH-MAT-R-91-28, Link\"oping University.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On the asymptotic behaviour of
solutions of ordinary differential equations with operator
coefficients} I, Preprint, LiTH-MAT-R-91-47, Link\"oping University.
\item Grachev, N.; Maz'ya, V. G. {\it Solvability of boundary integral
equations in a polyhedron}. Preprint, LiTH-MAT-R-91-50,
Link\"oping University.
\item Maz'ya, V. G. {\it A new approximation method and its
applications to
the calculation of volume potentials. Boundary point
method}. DFG-Kolloquium des DFG-Forschungsschwer-puntes
``Randelementmethoden'', 30 September-5 October, Schloss Reisenburg
(1991),
8.\hfill\break

{\bf 1992}
\item Kozlov, V. A.; Maz'ya, V. G.; Schwab, C. {\it On singularities
of
solutions of the displacement problem
of linear elasticity near the vertex of a cone}. Arch. Rational Mech.
Anal.
{\bf 119}:3, 197--227.
\item Maz'ya, V. G.; Rossmann, J. {\it On the Agmon-Miranda maximum
principle for solutions of
strongly elliptic equations in domains of ${\bf R}\sp n$ with conical
points}. Ann. Global Anal. Geom. {\bf 10}:2,
125--150.
\item Kozlov, V.; Maz'ya, V. {\it Solvability and asymptotic behaviour
of
solutions of ordinary differential equations
with variable operator coefficients}. Journ\'ees "\'Equations aux
D\'eriv\'ees Partielles" (Saint-Jean-de-Monts, 1992), Exp. no. V,
12 pp., \'Ecole Polytech., Palaiseau.
\item Maz'ya, V. G.; Rossmann, J. {\it Stable asymptotics of the
solution
to the Dirichlet problem
for elliptic equations of second order in domains with angular points
or
edges}. Operator calculus and spectral theory (Lambrecht,
1991), 215--224, Oper. Theory Adv. Appl., {\bf 57}, Birkh{\"a}user,
Basel.
\item Maz'ya, V. G.; Mahnke, R. {\it Asymptotics of the solution of a
boundary integral equation under a
small perturbation of a corner}. Z. Anal. Anwendungen {\bf 11}:2,
173--182.
\item Maz'ya, V. G.; Poborchii, S. V. {\it Imbedding theorems for
Sobolev
spaces in domains with cusps}. Preprint, LiTH-MAT-R-92-14,
Link\"oping University.
\item Maz'ya, V. G.; Slutskii, A. S. {\it An asymptotic solution of a
non-linear Dirichlet problem with strong singularity at the
corner point} I. Preprint, LiTH-MAT-R-92-15, Link\"oping University.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On the asymptotic behaviour of
solutions of ordinary differential equations with operator
coefficients} I, Preprint, LiTH-MAT-R-92-18, Link\"oping University.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On the asymptotic behaviour of
solutions of ordinary differential equations with operator
coefficients} III, Preprint, LiTH-MAT-R-92-29, Link\"oping University.


\item Maz'ya, V.; Rossmann, J. {\it On a problem of Babu\v ska (stable
asymptotics of the solution
to the Dirichlet problem for elliptic equations of second order in
domains
with angular points)}. Math. Nachr. {\bf 155},
199--220.\hfill\break

{\bf 1993}
\item Maz'ya, V. G.; H{\"a}nler, M. {\it Approximation of solutions of
the
Neumann problem in disintegrating domains}.
  Math. Nachr. {\bf 162}, 261--278.
\item Maz'ya, V. G.; Va{\u\i}nberg, B. R. {\it On ship waves}. Wave
Motion
{\bf 18}:1, 31--50.
\item Maz'ya, V.; Sulimov, M. {\it Asymptotics of solutions of
difference
equations with variable coefficients}.
Math. Nachr. {\bf 161}, 155--170.
\item Kresin, G. I.; Maz'ya, V. G. {\it Criteria for validity of the
maximum modulus principle
for solutions of linear strongly elliptic second order systems}.
Potential
Anal. {\bf 2}:1, 73--99.
\item Maz'ya, V. {\it Solvability and asymptotic behavior of solutions
of
ordinary differential equations with operator
coefficients}. Second International Conference on Mathematical and
Numerical Aspects of Wave Propagation (Newark, DE, 1993),
354--362, SIAM, Philadelphia, PA.
\item Maz'ya, V. G.; Slodichka, M. {\it Some time-marching algorithms
for
semilinear parabolic equations based upon approximate
approximations}. Preprint, LiTH-MAT-R-93-38, Link\"oping
University.\hfill\break

{\bf 1994}
\item Kozlov, V.; Maz'ya, V.; Rozin, L., {\it On certain hybrid
iterative
methods for solving
  boundary value problems}. SIAM J. Numer. Anal. {\bf 31}:1, 101--110.
\item Kozlov, V.; Maz'ya, V.; Fomin, A., {\it The inverse problem of
coupled thermoelasticity}.
Inverse Problems {\bf 10}:1, 153--160.
\item Maz'ya, V. G.; Rossmann, J. {\it On the behaviour of solutions
to the
Dirichlet problem for second order elliptic
equations near edges and polyhedral vertices with critical angles}. Z.
Anal. Anwendungen {\bf 13}:1, 19--47.
\item Kresin, G. I.; Maz'ya, V. G. {\it Criteria for validity of the
maximum modulus principle for solutions
  of linear parabolic systems}. Ark. Mat. {\bf 32}:1, 121--155.
\item Kozlov, V. A.; Maz'ya, V. G.; Parton, V. Z. {\it Asymptotics of
the
intensity factors for stresses induced by heat
  sources}. J. Thermal Stresses {\bf 17}:3, 309--320.
\item Maz'ya, V. {\it Approximate approximations}. The mathematics of
finite elements and applications
(Uxbridge, 1993), 77--104, Wiley, Chichester.
\item Kozlov, V. A.; Maz'ya, V. G.; Schwab, C. {\it On singularities
of
solutions to the Dirichlet problem of
  hydrodynamics near the vertex of a cone}. J. Reine Angew. Math. {\bf
456},
65--97.
\item Kozlov, V. A.; Maz'ya, V. G.; Movchan, A. B. {\it Asymptotic
analysis
of a mixed boundary value
problem in a multi-structure}. Asymptotic Anal. {\bf 8}:2, 105--143.
\item Carlsson, A.; Maz'ya, V., {\it On approximation in weighted
Sobolev
spaces and self-adjointness}.
Math. Scand. {\bf 74}:1, 111--124.
\item Maz'ya, V.; Karlin, V., {\it Semi-analytic time-marching
algorithms
for semi-linear
parabolic equations}. BIT {\bf 34}:1, 129--147.\hfill\break

{\bf 1995}
\item Maz'ya, V. G.; Poborchi{\u\i}, S. V. {\it On traces of functions
in
S. L. Sobolev spaces on the boundary of a thin cylinder}.
(Russian) Trudy Tbiliss. Mat. Inst. Razmadze Akad. Nauk Gruzii {\bf
99},
17--36.
\item Maz'ya, V.; Netrusov, Y., {\it Some counterexamples for the
theory of
Sobolev spaces on bad domains}.
Potential Anal. {\bf 4}:1, 47--65.
\item Maz'ya, V. G.; Verbitsky, I. E. {\it Capacitary inequalities for
fractional integrals,
with applications to partial differential equations and Sobolev
multipliers}. Ark. Mat. {\bf 33}:1, 81--115.
\item Kresin, G. I.; Maz'ya, V. G. {\it The norm and the essential
norm of
the double layer elastic and
hydrodynamic potentials in the space of continuous functions}. Math.
Methods Appl. Sci. {\bf 18}:14, 1095--1131.
\item Maz'ya, V.; Schmidt, G., {\it "Approximate approximations" and
the
cubature of potentials}. Atti Accad. Naz.
Lincei Cl. Sci. Fis. Mat. Natur. Rend. Lincei (9) Mat. Appl. {\bf
6}:3,
161--184.
\item Kozlov, V. A.; Maz'ya, V. G.; Movchan, A. B. {\it Asymptotic
representation of elastic fields in a multi-structure}.
Asymptotic Anal. {\bf 11}:4, 343--415.
\item Karlin, V.; Maz'ya, V., {\it Time-marching algorithms for
initial-boundary value problems
based upon "approximate approximations"}. BIT {\bf 35}:4, 548--560.
%\vfill\eject
\hfill\break

{\bf 1996}
\item Maz'ya, V.; Schmidt, G., {\it On approximate approximations
using
Gaussian kernels}. IMA J. Numer. Anal. {\bf 16}:1,
13--29.
\item Maz'ya, V. G.; Poborchi, S. V. {\it Extension of functions in
Sobolev
spaces on parameter dependent
domains}. Math. Nachr. {\bf 178}, 5--41.
\item Maz'ya, V.; Soloviev, A. A. {\it Boundary integral equations of
the
logarithmic
potential theory for domains with peaks}. Atti Accad. Naz. Lincei Cl.
Sci.
Fis. Mat. Natur. Rend. Lincei (9) Mat. Appl. {\bf 6}
(1995), no. 4, 211--236 (1996).
\item Kozlov, V. A.; Maz'ya, V. G. {\it Singularities in solutions to
mathematical physics problems
in non-smooth domains}. Partial differential equations and functional
analysis, 174--206, Progr. Nonlinear Differential Equations
Appl., {\bf 22}, Birkh{\"a}user, Boston, MA.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On "power-logarithmic"
solutions of
the Dirichlet problem
for elliptic systems in $K\sb d\times {\bf R}\sp {n-d}$, where $K\sb
d$ is
a $d$-dimensional cone}. Atti Accad. Naz. Lincei Cl. Sci.
Fis. Mat. Natur. Rend. Lincei (9) Mat. Appl. {\bf 7}:1,
17--30.\hfill\break

{\bf 1997}
\item Kozlov, V. A.; Maz'ya, V. G. {\it On "power-logarithmic"
solutions to
the Dirichlet problem
for the Stokes system in a dihedral angle}. Math. Methods Appl. Sci.
{\bf
20}:4, 315--346.
\item Karlin, V.; Maz'ya, V., {\it Time-marching algorithms for
nonlocal
evolution
equations based upon "approximate approximations"}. SIAM J. Sci.
Comput.
{\bf 18}:3, 736--752.
\item Livshits, M.; Maz'ya, V., {\it Solvability of the
two-dimensional
Kelvin-Neumann problem for a
submerged circular cylinder}. Appl. Anal. {\bf 64}:1-2, 1--5.
\item Maz'ya, V., {\it Unsolved problems connected with the Wiener
criterion}. The Legacy of
Norbert Wiener: A Centennial Symposium (Cambridge, MA, 1994),
199--208,
Proc. Sympos. Pure Math., {\bf 60}, Amer. Math. Soc.,
Providence, RI.
\item Maz'ya, V.; Soloviev, A. {\it $L\sb p$-theory of a boundary
integral
equation on a cuspidal contour}.
  Appl. Anal.{\bf  65}:3-4, 289--305.
\item Kozlov, V. A.; Maz'ya, V. G. {\it On "power-logarithmic"
solutions to
the Dirichlet problem for
the Stokes system in a dihedral angle}. Math. Methods Appl. Sci. {\bf
20}:4, 315--346.
\item Maz'ya, V. {\it Asymptotic theory of operator differential
equations
and its applications}.
Modern mathematical methods in diffraction theory and its applications
in
engineering (Freudenstadt, 1996), 163--173, Methoden
Verfahren Math. Phys., {\bf 42}, Lang, Frankfurt am Main.
\item Kuznetsov, N.; Maz'ya, V. {\it Asymptotic analysis of surface
waves
due to high-frequency
disturbances}. Atti Accad. Naz. Lincei Cl. Sci. Fis. Mat. Natur. Rend.
Lincei (9) Mat. Appl. {\bf 8}:1, 5--29.
\item Kozlov, V.; Maz'ya, V. G.; Rossmann, J. {\it Spectral properties
of
operator pencils generated
by elliptic boundary value problems for the Lam\'e system}. Rostock.
Math.
Kolloq. no. 51, 5--24.
\item Maz'ya, V. G. {\it Boundary integral equations on a contour with
peaks}. IABEM Symposium on Boundary Integral
Methods for Nonlinear Problems (Pontignano, 1995), 145--153, Kluwer
Acad.
Publ., Dordrecht.\hfill\break

{\bf 1998}
\item Maz' ya, V.; Soloviev, A. {\it $L\sb p$-theory of boundary
integral
equations on a contour with inward peak}. Z. Anal.
Anwendungen {\bf 17}:3, 641--673.
\item Maz' ya, V., Soloviev A. {\it $L\sb p$-theory of boundary
integral
equations on a contour with outward peak}. Integral
Equations Operator Theory {\bf 32}:1, 75--100.
\item Kresin, G.I., Maz'ya, V.G. {\it On the maximum modulus principle
for
linear parabolic systems with zero boundary data}.
Functional Differential Equations {\bf 5}:1--2, 165--181.
\item Maz'ya, V. {\it From Warschawski's conformal mapping theorem to
higher order multi-dimensional elliptic equations}. Analysis,
numerics and applications of differential and integral equations.
Pitman
Res. Notes Math. Ser., {\bf 379}, Longman, Harlow,
137--142.
\item Kozlov, V.; Maz'ya, V. {\it Comparison principles for nonlinear
operator differential equations in Banach spaces}. Birman's
70-th Anniversary Collection, American Mathematical Society,
Translations
2, {\bf 189}, 149--157.
\item Maz' ya, V., Soloviev A. {\it Integral equations of logarithmic
potential theory in H\"older spaces, on contours with peak}.
(Russian) Algebra i Analiz {\bf 10}:5, 85-142.
English translation in St. Petersburg Math. J. \textbf{10} (1999),
No.~5.
\item Kozlov, V.A., Maz'ya, V., Rossmann, J. {\it Conic singularities
of
     solutions to problems in hydrodynamics of a viscous fluid with a
free
     surface}. Math. Scand. {\bf 83}, 103-141.
\item Kresin, G.I., Maz'ya, V.G. {\it On the maximum principle with
respect to smooth norms for linear strongly coupled
parabolic systems}. Functional Differential Equations \textbf{5} No.
3-4
(1998), 349--376.
\hfill\break

{\bf 1999}
\item Maz'ya, V.; Netrusov, Y.; Poborchi, S. {\it Boundary values of
Sobolev functions on non-Lipschitz domains bounded by Lipschitz
surfaces}. Algebra i Analiz (Russian), {\bf 11}:1, 141--170.
\item Langer, M.; Maz'ya, V. {\it On $L^p$-contractivity of semigroups
generated by linear partial differential operators}.
J. Funct. Anal. 164 (1999), no. 1, 73--109.
\item Maz'ya, V.; Shaposhnikova, T. {\it On pointwise interpolation
inequalities for derivatives}. Mathematica Bohemica, \textbf{124}:2-3
(1999),
131--148.
\item Kozlov, V., Maz'ya, V. {\it Angle singularities of solutions to
the
Neumann problem for the two-dimensional Riccati
equation}. Asymptot. Anal. 19 (1999), no. 1, 57--79.
\item Kresin, G.I., Maz'ya, V.G. {\it Criteria for validity of the
maximum
norm principle for parabolic systems}. Potential
Analysis 10 (1999), {\bf 3}, 243--272.
\item Hansson, K.; Maz'ya, V.; Verbitsky, I. {\it Criteria of
solvability
for multidimensional Riccati's equations}. Ark. f\"or
Mat., {\bf 37}:1 (1999), 87--120.
\item Maz'ya, V. {\it On the Wiener-type regularity of a boundary
point for
the polyharmonic operator}. Appl. Anal. 71 (1999), {\bf 1-4},
149--165.
\item Maz'ya, V., Schmidt, G. {\it Approximate wavelets and the
approximation of pseudodifferential operators}. Appl.
Comput. Harmon. Anal. 6 (1999), {\bf 3}, 287--313.
\item Maz'ya, V. {\it On Wiener-type regularity of a boundary point
for
higher-order elliptic equations}. In Nonlinear Analysis, Function
Spaces and
Applications, vol.~6, Math. Inst. Czech Acad. of Sci., Prague, 1999,
19--155.
\item Ivanov, T., Maz'ya, V., Schmidt, G. {\it Boundary layer
approximate
approximations and cubature of potentials in domains}.
Adv. Comput. Math. 10 (1999), no. 3-4, 311--342.
\item Kozlov, V., Maz'ya, V., {\it Boundary singularities of solutions
     to quasilinear elliptic equations}, Journ\'ees \'Equations aux
\'eriv\'ees
     partilelles, 31 mai-4 juin 1999 GDR 1151 (CNRS), VII-1--9.
   131--148
\item Ivanov, T., Maz'ya, V., Schmidt, G.,
           {\it Construction of Basis Functions for High
            Order Approximate Approximations},
          Bonnet, M., S\"andig, A-M, Wendland, W. (Eds),
             Mathematical Aspects of Boundary Element Methods, Chapman
\&
             Hall/CRC Research Notes in Mathematics, London, 1999,
             165--177.
\item  Maz'ya, V., Schmidt, G.,
           {\it Boundary Layer Approximate Approximations for Cubature
of
             Potentials}, Bonnet, M., S\"andig, A-M, Wendland, W.
(Eds),
             Mathematical Aspects of Boundary Element Methods, Chapman
\&
             Hall/CRC Research Notes in Mathematics, London, 1999,
             191--202.
\item      Maz'ya, V., Soloviev, A.,
           {\it $L_p$-Theory of Direct Boundary Integral
            Equations on a Contour with Peak},
          Bonnet, M., S\"andig, A-M, Wendland, W. (Eds),
             Mathematical Aspects of Boundary Element Methods, Chapman
\&
             Hall/CRC Research Notes in Mathematics, London, 1999,
             203--214.

\item Maz'ya, V.
\title{Criteria for validity of the maximum
   modulus and the maximum norm principles
for solutions of linear parabolic systems}
\conference{Complex analysis and differential equations (Uppsala,
1997)}
\journal{Acta Univ. Upsaliensis Skr. Uppsala Univ. C Organ. Hist.}
\volume{64}
\publisher{Uppsala Univ., Uppsala}
\Year{1999}
\pages{249--254}

{\bf 2000}

\authors{Maz'ya, V., Slutski{\u\i}, A.}
\title{Asymptotic analysis of the Navier-Stokes system in a plane
domain
with
        thin channels}
\journal{Asympt. Anal.}
\volume{23}
\no{1}
\pages{59-89}
\jitem


\item Bj\"orn J., Maz'ya, V. {\it Capacity estimates for solutions of
the
Dirichlet problem for second order elliptic equations in
divergence form}
\journal{Potential Analysis}
\volume{12}
\no{1}
\pages{81--113}
\jitem


\item  Maz'ya, V., Shaposhnikova, T.
\title{Pointwise interpolation inequalities for Riesz and Bessel
potentials}
\journal{Analytical and computational methods in scattering and
applied
athematics}
\publisher{Chapman \& Hall/CRC Res. Notes Math., 417}
\pages{217--229}
\jitem


\authors{Karlin, V., Maz'ya, V., Movchan, A., Willis, J., Bullough,
R.}
\title{Numerical analysis of nonlinear hypersingular integral
equations of the Peierls type in dislocation theory}
\journal{SIAM J. Appl. Anal.}
\volume{60}
\no{2}
\pages{664--678}
\jitem



\authors{Maz'ya, V.; Shaposhnikova, T.}
\title{Traces and extensions of
multipliers in pairs of Sobolev spaces}
\journal{Operator Theory: Advances and Applications}
\volume{113}
\publisher{Birkh\"auser}
\Year{2000}
\pages{221--237}
\jitem

\authors{Maz'ya, V., Movchan, A.}
\title{Dynamic singular perturbation for multi-structures}
\journal{Applied Stochastic Models in Business and Industry}
\volume{16}
\pages{249-278}
\jitem


\authors{Maz'ya, V.}
\title{In memory of Gaetano Fichera}
\book{Problemi Attuali dell'Analisi e della Fisica Matematica}
\pages{1--4}
\publisher{Arcane}
\jitem

\authors{Kuznetsov, N., Maz'ya, V.}
\title{On a well-posed formulation of the two dimensional
Neumann--Kelvin
problem for a surface-piercing body}
\book{Problemi Attuali dell'Analisi e della Fisica Matematica}
\pages{77--109}
\publisher{Arcane}
\jitem






\item  Maz'ya, V., Shaposhnikova, T., {\it Maximal Banach Algebra in
spaces
     of multipliers between Bessel potential spaces},
     \series{Operator Theory: Advances and Applications}
     \conference{Siegfried Pr\"o{\ss}dorf Memorial Volume}
     \publisher{Birkh\"auser Verlag}
\volume{121}
\pages{352-365}
\jitem


\authors{Kuznetsov, N., Maz'ya, V.}
\title{Water-wave problem for a vertical shell}
\journal{Mathematica Bohemica} 
\volume{126}
\no{2}
\pages{411-420}
\jitem




\authors{Kresin, G.I., Maz'ya, V.G.}
\title{Fichera's maximum principle in elastostatics revisited and
related
topics}
\journal{Quaderni di Matematica}
\volume{7}
\pages{207--231}
\jitem

\authors{Kozlov, V., Maz'ya, V., Movchan, A.}
\title{Fields in nondegenerate 1D--3D elastic multistructures}
\journal{The Quarterly Journal of Mechanics and Applied Mathematics},
{\bf
4}:2, 177-212.
\jitem

\authors{Maz'ya, V.}
\title{The Wiener test for higher order elliptic equations}
\journal{Report No.~38, 1999/2000, Institut  Mittag-Leffler}
\pages{1--41}
\jitem

\authors{Kuznetsov, N.; Maz'ya, V.; Vainberg, B.}
\title{Lectures on linear time-harmonic water waves}
\journal{Technical report series, Dept. of Math., University of North
Carolina at Charlotte}
\pages{1--207}
\Year{July 2000.}

\hfill\break 

{\bf 2001}

\authors{Maz'ya, V., Schmidt, G.}
\title{On quasi--interpolation with non-uniformly distributed centers
on
      domains and manifolds}
\journal{J. Approx. Theory}
\volume{110}
\pages{125-145}
\jitem



\authors{Maz'ya, V.}
\title{In memory of Siegfried Pr\"o{\ss}dorf}
\journal{Operator Theory: Advances and Applications}
\volume{121}
\pages{4--8}
\publisher{Birkh\"auser Verlag}
\jitem

\authors{Kozlov, V., Maz'ya, V.}
\title{Boundary behavior of solutions to linear and nonlinear elliptic
equations in plane convex domains}
\journal{Mathematical Research Letters}
\volume{8}
\pages{1-5}
\jitem








\item Maz'ya, V., Soloviev, A.
{\it Boundary integral equations of plane elasticity theory
    in domains with peaks},
  Georgian Mathematical Journal {\bf 8}:3, 517-614. Addendum: 
  Georgian Mathematical Journal {\bf 9}:2, 403--404.

\hfill\break 
                                                        
{\bf 2002}

\item Maz'ya V.
{\it The Wiener test for higher order elliptic equations},
Duke Mathematical Journal,
{\bf 115}:3, 479--512.  

\authors{Maz'ya, V., Verbitsky, I.}
\title{Boundedness and compactness criteria for the one-dimensional
Schr\"odinger operator}
\journal{Function Spaces, Interpolation Theory and
    Related Topics (Lund, 2000)} 
\pages{369--382}
\publisher{de Gruyter, Berlin}
\jitem


\authors{Maz'ya, V., Rossmann J.}
\title{ Point estimates for Green's matrix to boundary value
problems for second order elliptic systems in a polyhedral cone}
\journal{Z. Angew. Math. Mech.}
\volume{82}
\no{5}
\pages{291-316}
\jitem


\authors{Maz'ya, V., Shaposhnikova, T.}
\title{An elementary proof of the Brezis and Mironescu theorem on the
composition operator in fractional Sobolev spaces}
\journal{Journal of Evolution Equations}
\volume{2}
\pages{113-125}
\jitem

\authors{Maz'ya, V., Shaposhnikova, T.}
\title{Sharp pointwise interpolation inequalities for derivatives}
 \journal{Journal of Functional Analysis and its
Applications}
\volume{36}
\no{1}
\pages{36-58}
\jitem

\item Maz'ya, V., Shaposhnikova, T.
{\it On the Bourgain, Brezis and Mironescu
  theorem concerning limiting embeddings of fractional Sobolev
spaces},
 Journal of Functional Analysis, 
{\bf 195},  230-238. 


\item Maz'ya, V., Shaposhnikova, T.
{\it On the Brezis and Mironescu
conjecture concerning
a Gagliardo-Nirenberg type inequality for fractional Sobolev norms}, 
Journal de Math{\'e}matiques Pures et Appliqu{\'e}es, 
 {\bf 81},  877-884. 





\authors{Kresin, G.I., Maz'ya, V.G.}
\title{Sharp parametric estimates for analytic and
harmonic functions related to Hadamard-Borel-Caratheodory
inequalities}
\journal{Functional Differential Equations}
\volume{9}
\no{1}
\pages{135--163}
\jitem

\item Maz'ya, V., Verbitsky, I. 
 {\it The Schr\"odinger operator on the energy space: boundedness and
compactness criteria}, Acta Mathematica, 
 {\bf 188}, 263--302. 


\item {Maz'ya, V.} {\it Wiener's test for higher order elliptic
equations}, 
Proceedings of the International Congress of Mathematicians, vol.3, 
Invited lectures, Beijing, pp. 189-195.


\authors{Maz'ya, V., Shaposhnikova, T.}
\title{A survey of  pointwise interpolation inequalities for integer
and fractional derivatives}
 \journal{Acoustics, Mechanics, and the Related Topics of Mathematical
Analysis}
\pages{212-221}
\publisher{World Scientific}
\jitem


\hfill\break 

{\bf 2003}

\authors{Kozlov, V.A., Maz'ya V.G.}
\title{Asymptotics of a singular solution to
the Dirichlet problem for elliptic equations with discontinuous
coefficients near the boundary}
\journal{Function Spaces, Differential Operators and Nonlinear
Analysis}
\pages{75-115}
\publisher{Birkh\"auser}
\jitem

\authors{Maz'ya, V., Schmidt, G., Wendland, W.}  
\title{On the computation of
multi-dimensional single layer harmonic potentials via approximate
approximations} 
\journal{Calcolo}
\volume{40}
\no{1}
\pages{33-53}
\jitem

\authors{Maz'ya, V., Rossmann, J.} 
\title{Weighted $L_p$ estimates of solutions to
boundary value problems for second order elliptic systems in
polyhedral domains}
\journal{Z. Angew. Math. Mech.}
\volume{83}
\no{7}
\pages{435-467}
\jitem       

\authors{Kresin, G.I., Maz'ya, V.G.} 
\title{Best constants in the Miranda-Agmon
inequalities for solutions of elliptic systems and the classical
maximum modulus principle for fluid and elastic half-spaces}
\journal{Applicable Analysis}
\volume{82}
\no{2}
\pages{157-185}
\jitem

\item Karlin, V., Maz'ya, V., Schmidt, G. 
{\it High accurate periodic solutions to the Sivashinsky equation}, 
Journal of Computational Physics, 
 {\bf 188}, 209-231. 

\item Hellsten H., Maz'ya V., Vainberg B. 
 {\it On the spectrum of waves produced by moving point sources  
on the sea surface, and a related inverse problem}, 
Wave Motion, 
{\bf 38}, 345-354. 



\authors{Maz'ya, V., Soloviev, A.}
\title{The direct method for boundary integral equations 
    on a contour with peak}
\journal{Georgian Mathematical Journal}
\volume{10}
\no{3}
\pages{573-593}
\jitem


\authors
{Maz'ya, V., Shaposhnikova, T.} 
\title{Erratum to: "On the Bourgain, Brezis and Mironescu
  theorem concerning limiting embeddings of fractional Sobolev
space''} 
\journal{Journal of Functional Analysis}
\volume{201}
\no{1}
\pages{298-300} 
\jitem


\authors{Maz'ya, V.}
\title{Applications of Isoperimetric and Isocapacitary Inequalities 
to the Theory of Sobolev Spaces}
\journal{Graduate Texts in Mathematics}
\volume{4}
\publisher{University of Helsinki}
\pages{1-39}
\jitem

\authors{Kozlov, V.A., Maz'ya, V.G.}
\title{Asymptotic formula for solutions to the
Dirichlet problem for elliptic equations with discontinuous
coefficients
near the boundary}
\journal{Ann. Scuola. Norm. Sup. Pisa}
\volume{2}
\no{3}
\pages{551-600}
\jitem


\authors{Maz'ya, V.}
\title{Lectures on Isoperimetric and Isocapacitary Inequalities 
in the Theory of Sobolev Spaces}
\journal{Contemporary Mathematics}
\volume{338}
\series{Heat Kernels and Analysis on Manifolds, Graphs, and Metric
Spaces}
\publisher{American Math. Society}
\pages{307-340}
\jitem


\authors{Kresin, G.I., Maz'ya, V.G.}
\title{Sharp  estimates for derivatives of analytic
 functions related to Hadamard-Borel-Carath{\'e}odory,
Carath{\'e}odory 
and Landau inequalities}
\journal{Funct. Diff. Equat.}
\volume{10}
\no{3-4}
\pages{493-533}
\jitem




 




\item Maz'ya, V., Rossmann, J.
 {\it Estimates for Green's matrix of boundary value problems for 
the Stokes system in a polyhedral cone}
 (Preprint ESI 1419). 




{\bf 2004}

\authors{Maz'ya, V., Elschner, J., Rehberg, J., Schmidt, G.}
\title{Solutions for quasilinear, nonsmooth evolution systems in
$L^p$}
\journal{Archive for Rat. Mech. Analysis}
\volume{171}
\no{2}
\pages{219-262}
\jitem

\authors{Maz'ya, V., Rossmann, J.} 
\title{Schauder estimates for solutions to
boundary value problems for second order elliptic systems in
polyhedral domains} 
\journal{Appl. Analysis}
\volume{83}
\no{3}
\pages{271-308}
\jitem


\authors{Kondratiev V., Maz'ya V., Shubin M.} 
\title{Discretness of spectrum and
strict positivity criteria for magnetic Schr\"odinger operators} 
\journal{Comm. Partial Differential Equations}
\volume{29}
\no{3-4}
\pages{489-521}
\jitem


\authors{Maz'ya, V., Verbitsky, I.}
\title{The form boundedness criterion for the relativistic
Schr\"odinger operator} 
\journal{Ann. Inst. Fourier}
\volume{54}
\no{2}
\pages{317-339} 
\jitem

\authors{Maz'ya, V.}
\title{Remembering Erhard Meister}
\journal{Operator Theoretical Methods and Applications to Mathematical
Physics: The Erhard Meister Memorial Volume}
\publisher{Birkh\"auser}
\pages{83-87}
\jitem


\authors{Maz'ya, V., Shaposhnikova, T.}
\title{Characterization of 
multipliers in pairs of Besov spaces}
\journal{Operator Theoretical Methods and Applications to Mathematical
Physics: The Erhard Meister Memorial Volume}
\publisher{Birkh\"auser}
\pages{365-387}
\jitem

\authors{Kozlov, V., Maz'ya, V.}
\title{Sharp conditions for the classical asymptotic behaviour near a
point for solutions to
quasilinear elliptic systems}
\journal{Asymptotic Analysis}
\volume{38} 
\no{2}
\pages{143-165}
\jitem

\item Maz'ya, V., Slutskii A.
 {\it Asymptotic solution to the Dirichlet problem for a
two-dimensional Riccati's type equation
near a corner point}, 
 \journal{Asymptotic Analysis}
 \volume{39}
 \no{2}
 \pages{169-185}
 \jitem


\item Kozlov, V., Maz'ya, V.
 {\it An asymptotic theory of higher-order operator differential
equations with nonsmooth 
nonlinearities}
\journal{ Journal of Functional Analysis}
\volume{217}
\pages{448-488}
\jitem

\authors{Filippas, S., Maz'ya, V., Tertikas, A.}
\title{Sharp Hardy-Sobolev inequalities}
\journal{C.R. Acad. Sci. Paris}
\volume{339}
\no{7}
\pages{483-486}
\jitem

\authors{Kresin, G., Maz'ya, V.}
\title{Sharp pointwise estimates for analytic functions by $L_p$-norm
of 
real part}
\journal{Complex Variables}
\volume{49}
\no{14-15}
\pages{997--1023}
\jitem


\authors{Lanzara, F., Maz'ya, V., Schmidt, G.}
\title{Numerical solution of the Lippmann-Schwinger equation by
approximate approximations}
\journal{Journal of Fourier Analysis and
Applications}
\volume{10}
\no{6}
\pages{645--660}
\jitem







\smallskip

{\bf 2005}





\authors{Maz'ya V., Shaposhnikova, T.}
\title{Traces of multipliers in
pairs of weighted Sobolev spaces}
\journal{Journal of Function Spaces and Applications}
\volume{3}
\pages{91--115}
\jitem



\authors{Maz'ya V., Shaposhnikova, T.}
\title{Higher regularity in the classical layer potential theory for
Lipschitz domains} 
\journal{Indiana University Mathematics Journal}
\volume{54} 
\no{1}
\pages{99--142}
\jitem

\authors{Maz'ya, V.}
\title{Conductor and capacitary inequalities for functions on
topological
spaces and their applications to Sobolev type imbeddings}
\journal{Journal of Functional Analysis}
\volume{224}
\no{2}
\pages{408--430}
\jitem


\authors{Kozlov,  V., Maz'ya, V.} 
\title{Asymptotic formula for solutions to elliptic
equations near the Lipschitz boundary} 
\journal{ Ann. Mat. Pura ed Appl.}
\volume{184}
\no{2}
\pages{185--213}
\jitem

\authors{Maz'ya, V., Shubin, M.}
\title{Discreteness of spectrum and positivity criteria for
Schr\"odinger operators}
\journal{Annals of Mathematics}
\volume{162}
\pages{1--24}
\jitem


\authors{Cialdea, A., Maz'ya, V.}
\title{Criterion for the $Lp$-dissipativity of second order
differential operators with complex coefficients}
\journal{Journal de Math{\'e}matiques Pures et Appliqu{\'e}es}
\volume{84}
\pages{1067-1100} 
\jitem

\authors{Gibiansky E., Maz'ya, V., Movchan A.}
\title{Three-scale asymptotics for a diffusion problem coupled with
the wave equation}
\journal{Applicable Analysis}
\volume{84}
\no{6}
\pages{585--600}
\jitem

\item Maz'ya, V., Verbitsky, I.
 {\it Infinitesimal form boundedness and Trudinger's subordination 
for
the Schr\"odinger operator} 
\journal{Inventiones Mathematicae}
\volume{161}
\pages{81--136}
\jitem 





 \authors{Maz'ya, V., Mitrea, M., Shaposhnikova, T.}
\title{The Dirichlet problem in Lipschitz domains with boundary data in Besov spaces for higher order elliptic systems with rough coefficients}
\ (arXiv.math.AP/0505372)


\authors{Maz'ya, V., Shubin, M.}
\title{Can one see the fundamental frequency of a drum?}
\journal{Letters in Mathematical Physics}
\volume{74}
\no{2}
\pages{135--151}
\jitem



\authors{Maz'ya, V., Rossmann, J.} 
\title{Pointwise estimates for Green's kernel of a mixed boundary
value problem to the Stokes system in a polyhedral cone}
 \journal{Math. Nachr.}
 \volume{278}
 \no{15}
 \pages{1766--1810}
\jitem

\smallskip

{\bf 2006}

\authors{Maz'ya, V., Verbitsky, I.}
\title{Form boundedness of the general second order differential
operator}
\journal{ Comm. Pure Appl. Math.}
\volume{59}  
\no{9}
\pages{1286--1329}
\jitem

\authors{ Mazya, V., J. Rossmann, J.} 
\title{Schauder estimates for solutions to a mixed boundary value problems for Stokes system in polyhedral domains}
\journal{ Math. Methods Appl. Sci.}
\volume{29}
\no{9}
\pages{965--1017}
\jitem

  \authors{Maz'ya, V.,  Movchan, A.}
  \title{Uniform asymptotic formulae for Green's functions in regularly and singularly perturbed domains}
 \journal{ C. R. Math. Acad. Sci. Paris}
 \volume{343} 
 \no{3}
 \pages{185--190}
  \jitem

\authors{Maz'ya, V.}
\title{ Conductor inequalities and criteria for Sobolev type two-weight imbeddings}
\journal{J. Comput. Appl. Math.}
\volume{194}
\no{1}
\pages{94--114}
\jitem

\authors{Filippas, S.,  Maz'ya, V., Tertikas, A.}
\title{On a question of Brezis and Marcus}
\journal{Calc. Var. Partial Differential Equations}
\volume{25}
\no{4}
\pages{491--501}
\jitem





\authors{Cialdea, A.,  V. Maz'ya, V.}
\title{Criteria for the $L^p$-dissipativity of systems
 of second order differential equations}
\journal{Ric. Mat.}
\volume{55}
\no{2}
\pages{233-265}
\jitem

 \authors{Mazya, V., Poborchi, S.}
\title{Embedding theorems for Sobolev spaces on a domains with a peak  and in  H\"older domains}
\journal{Algebra i Analiz}
\volume{18}
\no{4}
\pages{95-126}
\jitem


\smallskip

{\bf 2007}

\authors{Maz'ya, V.}
\title{Analytic criteria in the qualitative spectral analysis of the Schr\"odinger operator}
\journal{ Spectral theory and mathematical physics: a Festschrift in honor of Barry Simon's 60th birthday,   Proc. Sympos. Pure Math.,  Part 1, Amer. Math. Soc.,  Providence, RI}
\volume{76}
\pages{257--288}
\jitem

 \authors{Maz'ya, V.,  McOwen, R.}
\title{Asymptotics for solutions of elliptic equations in double divergence form}
\journal{Comm. in Partial Diff. Eq.}
\volume{32}
\pages{191-207}
\jitem

\authors{Filippas, S.,  Maz'ya, V.,  Tertikas, A.}
\title{Critical Hardy-Sobolev inequalities}
\journal{Journal de Math. Pure et Appl.}
\volume{87}
\pages{37-56}
\jitem

\authors{Maz'ya, V., Poborchi, S.}
\title{On solvability of the Neumann problem in an energy space for a domain with peak}
\journal{Georgian Math. J.}
\volume{14}
\no{3}
\pages{499-518}
\jitem

\authors{Maz'ya, V.,  Rossmann, J.}
\title{$L\sb p$ estimates of solutions to mixed boundary value problems for the
 Stokes system in polyhedral domains}
\journal{ Math. Nachr.}
\volume{ 280} 
\no{7}
\pages{ 751-793}
\jitem 


  
  
   \authors{Maz'ya, V.,  Movchan, A.}
  \title{Uniform asymptotic formulae for Green's kernels in regularly and singularly perturbed domains}
  \journal{ J. Comput. Appl. Math.}
 \volume{208}
 \no{1}
 \pages{194-206}
\jitem 

\authors{Maz'ya, V.,  Schmidt, G.}
 \title{Potentials of Gaussians and approximate wavelets}
 \journal{Math. Nachr.}
 \volume{280}  
 \no{9-10}
 \pages{1176--1189}
\jitem

\ ( arXiv:math. SP/0601057)

\authors{Kresin, G., Maz'ya, V.}
\title{Sharp Bohr's type real part theorem}
\journal{Comput. Methods Funct. Theory}
\volume{7}
\no{1}
\pages{151-165}
\jitem

\authors{Maz'ya, V.}
\title{A new type of integral equations related to the co-area formula (reduction of dimension in multi-dimensional integral equations)}
\journal{ J. Funct. Anal.}
\volume{245}
\no{2}
\pages{ 493--504}
\jitem

\authors{Lanzara, F., Maz'ya, V., Schmidt, G.}
\title{Approximate approximations from scattered data}  
\journal{J. Approx. Theory}
\volume{145}
\no{2}
\pages{141--170}
\jitem

\authors{Kresin, G., Maz'ya, V.}
\title{Sharp pointwise estimates for solutions of strongly elliptic second order systems with boundary data from $L_p$.}
\journal{Appl. Analysis}
\volume{86}
\no{7}
\pages{783-805}
\jitem

 
 \authors{Luo, G., Maz'ya, V.}
 \title{Weighted positivity of second order elliptic systems}
 \journal{Potential. Anal.}
 \volume{27}
 \no{3}
 \pages{251-270}
\jitem

\authors{Maz'ya, V. G.,  Movchan, A. B.,  Nieves, M. J.}
\title{Uniform asymptotic formulae for Green's tensors in elastic singularly perturbed domains}
\journal{Asymptot. Anal.}
\volume{52} 
\no{3-4}
\pages{173-206} 
\jitem

 \authors{Maz'ya, V.}
 \title{Bourgain-Brezis type inequality with explicit constants}
 \journal{Interpolation Theory and Applications, Contemporary Mathematics}
\volume{445}  
\pages{247-264}
 \jitem 

 \authors{Lanzara, F.,  Maz'ya, V., Schmidt, G.}
  \title{ Approximate approximations on nonuniform grids}
   \journal{ Matematiche (Catania)}
   \volume{ 62}
    \no{2}
    \pages{ 303--318}
 \jitem 
 
\smallskip

{\bf 2008}

 \authors{Maz'ya, V.,  Poborchi, S.}
  \title{On solvability of the Neumann problem for 
 a planar domain with peak}
  \journal{Vestnik SPbGU} 
 \volume{41} 
   \no{2}
   \pages{145--160}
 \jitem 
 
 
  \authors{Maz'ya, V.,  Poborchi, S.}
  \title{On solvability of the Neumann problem in 
 a domain with peak}
  \journal{  (Russian)  Algebra and Analysis}
   \volume{ 20} 
   \no{5}
     \pages{108--153}
     \jitem  

\authors{Lanzara, F.,  Maz'ya, V., Schmidt, G.}
\title{Approximate approximations with data on a perturbed  uniform grid}
\journal{Z. Anal. Anwend.} 
\volume{27}
 \no{3} 
 \pages{323--338}
 \jitem 

\authors{Costin, O., Maz'ya, V.}
\title{Sharp Hardy-Leray inequality for axisymmetric divergence-free fields}
\journal{Calc. Var. Partial Differential Equations}
 \volume{32}
 \no{4}
 \pages{ 523--532}
\jitem 

\authors{Cianchi, A., Maz'ya, V.}
\title{Neumann problems and isocapacitary inequalities}
\journal{J. Math. Pures Appl.}
\volume{89}
\pages{71--105}
\jitem


\authors{ Maz'ya,  V., Shaposhnikova, T.}
\title {A Collection of sharp dilation invariant integral inequalities
for differentiable functions} 
\book{Sobolev Spaces in Mathematics I. Sobolev Type Inequalities}
\pages{223--248}
\publisher{Springer}
\jitem


\authors{ Costea,  S., Maz'ya,  V.}
\title {Conductor inequalities and criteria for Sobolev-Lorentz two-weight inequalities} 
\book{Sobolev Spaces in Mathematics II. Applications in Analysis and Partial Differential Equations}
\pages{103--122}
\publisher{Springer}
\jitem


\authors{ Maz'ya,  V., Movchan, A.}
\title {Uniform asymptotics  of Green's kernels for mixed and Neumann problems in domains with small holes and inclusions} 
\book{Sobolev Spaces in Mathematics III. Applications in Mathematical Physics}
\pages{277--316}
\publisher{Springer}
\jitem

 \authors{Maz'ya,V.,  Movchan, A.,  Nieves, M.}
\title{Uniform asymptotic formulae for Green's tensors inelastic singularly
perturbed domains with multiple inclusions}
 \journal{Rendiconti Accademia Nazionale
delle Scienze detta dei XL, Memorie di Matematica e Applicazioni, 124}
\volume{XXX}
\no{1}
\pages{103-158}
\jitem


\authors{Lang, J., Maz'ya, V.} 
\title {Essential norms and localization moduli of Sobolev
embeddings for general domains}
  \journal{J.  London Math. 
Soc.}
\volume{78}
 \no{2}
 \pages{ 373--391}
\jitem

\authors{Maz'ya,  V., Rossmann,  J.}
\title {Mixed boundary value problems for the stationary Navier-Stokes System in
polyhedral domains}
 \journal{Arch. Rational Mech. Anal.}
\no{DOI 10.1007/s00205-008-0171-z}
\jitem






\authors{Mayboroda, S., Maz'ya, V.}
\title{Boundedness of the Hessian of a biharmonic function in a convex domain}
 \journal{Communications on Partial Differential Equations}
 \volume{33}
 \no{8}
  \pages{1439--1454}
\jitem


  \authors{Maz'ya, V., Movchan, A.}
 \title{Uniform asymptotic approximations of Green's functions in a long rod}
 \journal{Math. Meth. Appl. Sci.}
 \volume{31}
 \pages{2055--2068} 
\jitem

\smallskip

{\bf 2009}

\authors{Mayboroda, S., Maz'ya, V.}
\title{ Boundedness of the gradient of a solution and Wiener test of order one for the biharmonic equation}
\journal{ Invent. Math.}
\volume{175} 
\no{2}
\pages{287--334}
\jitem
  
  \authors{Maz'ya, V.}
  \title{Boundedness of the gradient of a solution to the Neumann-Laplace problem in a convex domain} 
  \journal{C.R. Acad. Sci. Paris, Ser. I}
  \volume{347}
  \pages{517-520}
  \jitem 

\authors{Kozlov, V. A.,  Maz'ya, V. G.,  Fomin, A. V.}
 \title{Uniqueness of the solution of an inverse problem of thermoelasticity}
   \journal{Zh. Vychisl. Mat. Mat. Fiz. (Russian)}
   \volume{49}
    \no{3}
    \pages{542--548}
    \jitem
    
    
  \authors{Maz'ya, V., Shaposhnikova, T.}
   \title{A collection of sharp dilation invariant integral inequalities for differentiable functions}
   \book{ Sobolev spaces in mathematics. I, Int. Math. Ser. (N. Y.), 8, Springer, New York}
     \pages{223--247}
     \jitem 
    
  \authors{Maz'ya, V.}
   \title{Integral and isocapacitary inequalities}
   \book{Linear and complex analysis,  Amer. Math. Soc. Transl. Ser. 2, 226, Amer. Math. Soc., Providence, RI}   
\pages{85--107}
\jitem

\authors{Jin, T., Maz'ya, V., Van Schaftingen, J.}
\title{Pathological solutions to elliptic problems in divergence form with continuous coefficients}
\journal{C. R. Math. Acad. Sci. Paris}
\volume{ 347}
\no{13-14}
\pages{773--778}
\jitem 


\authors{Maz'ya, V., Movchan, A.}
\title{Uniform asymptotics of Green's kernels for mixed and Neumann problems in domains with small holes and inclusions}
\book{Sobolev Spaces in Mathematics. III, Int. Math. Ser. (N. Y.), 10, Springer, New York}
 \pages{277--316}
 \jitem
 
 
\authors{Maz'ya, V.,  Rossmann, J.}
\title{A maximum modulus estimate for solutions of the Navier-Stokes system in domains of polyhedral type}
\journal{Math. Nachr.}
\volume{282}
\no{3}
\pages{459--469}
\jitem

\authors{Costea, S.,  Maz'ya, V.}
\title{Conductor inequalities and criteria for Sobolev-Lorentz two-weight inequalities}
\book{Sobolev spaces in mathematics. II,  Int. Math. Ser. (N. Y.), 9, Springer, New York}
\pages{103--121}
\jitem

\authors{Kondratiev, V., Maz'ya, V., Shubin, M.,}
\title{Gauge optimization and spectral properties of magnetic Schr\"odinger operators}
 \journal{Communications in Partial Differential Equations}
 \volume{34}
 \no{10}
 \pages{1127--1146} 
\jitem


\authors{Maz'ya, V., Mitrea, M., Shaposhnikova, T.} 
\title{The nonhomogeneous Dirichlet problem for the Stokes system in Lipschitz domains with unit normal close to VMO}
\journal{Funct. Anal. Appl.}
\volume{43}
\no{3}
\pages{217--235}
\jitem

 \authors{Maz'ya, V.}
 \title{On the boundedness of first derivatives for solutions to the Neumann-Laplace problem in a convex domain}
 \journal{J. Math. Sci. (N. Y.)} 
 \volume{159} 
 \no{1}
 \pages{104--112}
\jitem

\medskip

{\bf 2010}

\authors{Maz'ya, V.,  Poborchii, S.}
\title{On solvability of boundary integral equations of potential theory for a multidimentional cusp domain}
\journal{J. of  Math. Sciences}
\volume{164}
\no{3}
\pages{403--414}
\jitem

\authors{Cialdea, A., Maz'ya, V.}
\title{A quasicommutativity property of the Poisson and composition operators}
\journal{J. of  Math. Sciences}
\volume{164}
\no{3}
\pages{415--426}
\jitem

\authors{Maz'ya, V.}
\title{Estimates for differential operators of vector analysis involving $L^1$-norm}
\journal{J. Eur. Math. Soc.}
\volume{12}
\no{1}
\pages{221--240}
\jitem


\authors{Kresin, G.,  Maz'ya, V.}
\title{Optimal estimates for the gradient of harmonic functions in the multidimensional half-space}
\book{Discrete and Continuous Dynamical Systems, A special issue dedicated to Louis Nirenberg on the occasion of his 85th birthday, AIMS}
\volume{28}
\no{2}
\pages{425--440}
\jitem

\authors{Maz'ya, V., Mitrea, M., Shaposhnikova, T.} 
\title{The Dirichlet problem in Lipschitz domains for higher order elliptic systems with rough coefficients}
\journal{Journal d'Analyse Math\'ematique}
\volume{110}
\pages{167--239}
\jitem

\authors{Luo, G., Maz'ya, V.}
\title{Wiener type regularity of a boundary point for the 3D Lam\'e system}
\journal{Potential Anal.}
\volume{32}
\no{2}
\pages{133 -- 151}
\jitem

\authors{Maz'ya, V.,  Movchan, A.}
\title{Asymptotic treatment of perforated domains without homogenization}
\journal{Math. Nachr.}
\volume{283} 
\no{1}
\pages{104--125}
\jitem

\authors{Alvino, A.,  Cianchi, A.,  Maz'ya, V.,  Mercaldo, A.}
\title{Well-posed elliptic Neumann problems involving irregular data and domains}
\journal{Ann. Inst. H. Poincar\'e Anal. Non Lin\'eaire}
\volume{27}
\no{4}
\pages{1017--1054}
\jitem


\authors{Maz'ya, V.,  McOwen, R.}
\title{On the fundamental solution of an elliptic equation in nondivergence form}
\book{Nonlinear Partial Differential Equations and Related Topics, Amer. Math. Soc. Transl. Ser. 2}
 \volume{229}
 \pages{145--172}
\jitem 

\authors{Maz'ya, V., Movchan, A., Nieves, M.}
\title{Green kernels for transmission problems in bodies with small inclusions}
 \book{Operator Theory and its Applications. In memory of V.B. Lidsky (1924--2008), Amer. Math. Soc. Transl. Ser. 2}
 \volume{231}
\pages{127--160}
\jitem 

\medskip

{\bf 2011}

\authors{Alvarado, R., Brigham, D., Maz'ya, V., Mitrea, M., Ziade, E.}
\title{Sharp geometric maximum principles for semi-elliptic operators with singular drift}
\journal{Math. Res. Lett.}
\volume{18}
\no{4}
\pages{613--620}
\jitem


\authors{Lanzara, F.,  Maz'ya, V.,  Schmidt, G.}
\title{On the fast computation of high dimensional volume potentials}
\journal{Math. Comp.}
\volume{80}
\no{274}
\pages{887--904}
\jitem

\authors{Cianchi, A.,  Maz'ya, V.}
\title{Global Lipschitz regularity for a class of quasilinear elliptic equations}
\journal{Comm. Partial Differential Equations}
\volume{36}
\no{1}
\pages{100--133}
\jitem


\authors{Maz'ya, V., McOwen, R.}
\title{Differentiability of solutions to second-order elliptic equations via dynamical systems}
\journal{J. Diff. Equations}
\volume{250}
\pages{1137 -- 1168}
\jitem

\authors{Maz'ya, V., Shaposhnikova, T., Tampieri, D.}
\title{Solomon Grigoryevich Mikhlin}
\journal{MacTutor, March 2011}
\pages{1--5}
\jitem 



\authors{Maz'ya, V., Shaposhnikova, T.}
\title{Recent progress in elliptic equations and systems of arbitrary order with rough coefficients in Lipschitz domains}
\journal{Bulletin of Mathematical Sciences}
\volume{1} 
\no{1}
\pages{33--77}
\jitem

\authors{Galaktionov, V.A., Maz'ya, V.} 
\title{Boundary characteristic point regularity for semilinear reaction-diffusion equations: towards an ODE criterion}
\journal{J. of Mathematical Sciences}
\volume{175}
\no{3}
\jitem

\authors{Maz'ya, V., Shaposhnikova,T.}
 \title{Brezis-Gallouet-Wainger type inequality for irregular domains}
 \journal{Complex Variables and Elliptic Equations}
 \volume{56}
 \no{10}
 \pages{991--1002} 
 \jitem

\authors{Maz'ya, V., Poborchi, S.}
\title{Existence and uniqueness of the energy solution to the Dirichlet problem for the Laplace equation in the exterior of a multi-dimensional paraboloid}
\journal{ J. of Math. Sciences}
\volume{172}
\no{4}
\pages{532--554}
\jitem
 
\authors{Kamotski, I.,  Maz'ya, V.}
\title{On the third boundary value problem in domains with cusps}
\journal{J. of Math. Sciences}
\volume{173}
\no{5}
\pages{609-631}
\jitem

\authors{Alvarado, R., Brigham, D., Maz'ya, V., Mitrea, M., Ziade, E.}
\title{On the regularity of domains satisfying a uniform hour-glass condition and sharp version of the Hopf-Oleinik boundary point principle}
\journal{J. of Math. Sciences}
\volume{176}
\no{3}
\pages{281--360}
\jitem


\authors{Kresin, G., Maz'ya, V.}
\title{Sharp real part theorems in the upper halfplane and similar estimates for harmonic functions}
\journal{
J. of Math. Sciences}
\volume{179}
\no{1}
\pages{144--163} 
 \jitem

 
\medskip

{\bf 2012}

 \authors{Kresin, G., Maz'ya, V.}
\title{Sharp real part theorems for higher order derivatives}
\journal{
J. of Math. Sciences}
\volume{181}
\no{2}
\pages{107--125} 
 \jitem

\authors{Galaktionov, V.A., Maz'ya, V.}
\title{Boundary characteristic point regularity for Navier-Stokes equations: Blow-up scaling and Petrovskii-type criterion (a formal approach)}
\journal{Nonlinear Anal.}
\volume{75}
\no{12}
\pages{4534--4559}
 \jitem
 
\authors{Maz'ya, V., Movchan, A.}
\title{Uniform asymptotics of Green's kernels in perforated domains and meso-scale approximations}
\journal{Complex Var. Elliptic Equ.}
\volume{57}
\no{2--4} 
\pages{137--154} 
 \jitem 

\authors{Maz'ya, V.}
\title{Representations and estimates for inverse operators in the harmonic potential theory for polyhedra}
\journal{Atti Accad. Naz. Lincei Cl. Sci. Fis. Mat. Natur. Rend. Lincei (9) Mat. Appl.}
\volume{23}
\no{3}
\pages{229--258}
 \jitem
 
\authors{Grachev, N.,  Maz'ya, V.}
\title{Estimates for kernels of inverse operators of integral equations of elasticity theory on surfaces with conic points}
\journal{J. Math. Sci. (N. Y.)}
\volume{186}
\no{2}
\pages{179--208} 
 \jitem

\authors{Grachev, N.,  Maz'ya, V.}
\title{Invertibility of boundary   integral operators of elasticity on surfaces with conic points}
\journal{J. Math. Sci. (N. Y.)}
\volume{186}
\no{2}
\pages{209--233}
 \jitem
 
 \authors{Cianchi, A.,  Maz'ya, V.}
 \title{Boundedness of solutions to the Schr\"odinger equation under Neumann boundary conditions}
 \journal{J. Math. Pures Appl.}
 \volume{98} 
 \no{6}
 \pages{654--688}
  \jitem 

 \authors{Jaye, B. J.,  Maz'ya, V. G.,  Verbitsky, I. E.}
 \title{Existence and regularity of positive solutions of elliptic equations of Schr\"odinger type}
 \journal{J. Anal. Math.}
 \volume{118}
 \pages{ 577--621}
  \jitem 

\medskip

{\bf 2013}

 \authors{Jaye, B. J.,  Maz'ya, V.,  Verbitsky, I.E.}
 \title{Quasilinear elliptic equations and weighted Sobolev-Poincar\'e inequalities with distributional weights}
 \journal{Adv. Math.}
 \volume{232}
 \no{1}
 \pages{513--542}
 \jitem

 \authors{Grachev, N.V., Maz'ya, V.}
 \title{Solvability of boundary integral operators of elasticity on surfaces with conic points}
 \journal{J. Math. Sci. (N. Y.)}
\volume{191}
\no{2}
\pages{178--192}
 \jitem
 
 
 
  \authors{Grachev, N.V., Maz'ya, V.}
 \title{Solvability of a boundary integral equation on a polyhedron}
 \journal{J. Math. Sci. (N. Y.)}
\volume{191}
\no{2}
\pages{193--213}
 \jitem

 \authors{McOwen, R., Maz'ya, V.}
 \title{Second order differentiability for solutions of elliptic equations in the plane}
 \journal{J. Math. Sci. (N. Y.)}
\volume{191}
\no{2}
\pages{243--253}
 \jitem



\authors{Kamotski, I. V., Maz'ya, V. G.}
\title{On the linear water wave problem in the presence of a critically submerged body}
\journal{ SIAM J. Math. Anal.}
\volume{44}
\no{6}
\pages{4222--4249}
\jitem


\authors{Lanzara, F., Maz'ya ,V., Schmidt, G.}
\title{Fast cubature of volume potentials over rectangular domains 
by approximate approximations}
 \journal{Applied and Computational Harmonic Analysis}
\jitem

\authors{Cianchi, A., Maz'ya, V.}
\title{Bounds for eigenfunctions of the Laplacian on noncompact Riemannianmanifolds}
\journal{Amer. J. Math.}
\volume{135}
\no{3}
\pages{579--635}
\jitem

\medskip

{\bf 2014}

\authors{Mayboroda, S.,  Maz'ya, V.}
\title{Regularity of solutions to the polyharmonic equation in general domains}
\journal{Inventiones Mathematicae} 
\volume{196}
\no{1}
\pages{1--68}
\jitem

\authors{Cianchi, A., Maz'ya, V.}
\title{Gradient regularity via rearrangements for p-Laplacian type elliptic boundaryvalue problems}
\journal{ J. Eur. Math. Soc.}
\volume{16}
\no{3}
\pages{571--595}
\jitem

\authors{Cianchi, A., Maz'ya, V. G.}
\title{Global boundedness of the gradient for a class of nonlinear elliptic systems}\journal{Arch. Ration. Mech. Anal.}
\volume{212}
\no{1}
\pages{129--177}
\jitem
\authors{Lanzara, F.; Maz'ya, V.; Schmidt, G.}
\title{Fast cubature of volume potentials over rectangular domains byapproximate approximations}
\journal{Appl. Comput. Harmon. Anal.}
\volume{36}
\no{1}
\pages{167--182}
\jitem

\bigskip

\textbf{\large Books edited}

\item Maz'ya, V., Nikol'skii, S.M. (Editors) {\it Analysis IV: Linear and Boundary Integral Equations}, Encyclopedia of Mathematical Sciences, Spronger, 1991.

\item Maz'ya, V. (Editor)
 {\it Sobolev Spaces in Mathematics},  I. Sobolev Type Inequalities, Springer,  2008.

\item Maz'ya, V. (Editor)
 {\it Sobolev Spaces in Mathematics},  II. Applications in Analysis and Partial Differential Equations, Springer,  2008.


\item  Agranovsky, M.,  Ben-Artzi, M.,  Galloway, G., 
 Karp, L.,  Maz'ya, V.,  Reich, S.,  Shoikhet, D., 
  Weinstein, G.,  Zalcman, L. 
(Editors) {\it Complex Analysis and
Dynamical Systems V, 
Fifth International Conference on
Complex Analysis and Dynamical Systems
May 22--27, 2011
Akko (Acre), Israel}, Contemporary Mathematics, v.591, American Mathematical Society
Providence, Rhode Island

% \authors{}
% \title{}
% \journal{}
% \jitem
\end{enumerate}

Last update: 2014--8--30

\end{document}


